---
title: "Patient Survey Accrual Report Version 2"

date: "`r format(Sys.Date(), '%m-%d-%Y')`"

format: 
  docx:
    toc: true
    embed-resources: true
    reference-doc: "D:/custom-reference-doc.docx"

execute: 
  echo: false
---

```{r}
# /////////////////////////////////////////////////////////////////////////////
# Carlos Rodriguez, PhD. CU Anschutz, Dept. of Family Medicine

# Long COVID - Patient Accrual Report

# This file is designed to generate a report indicating which patients have 
# completed their surveys in the AHRQ Long COVID project.
```

```{r, message=FALSE, warning=FALSE}
#| echo: false
library(magrittr, include = "%<>%")
library(tidyverse)
library(gtsummary)
library(dfmtbx)
```

```{r, message=FALSE, warning=FALSE}
# Loads pasc severity data and loads functions for displaying the tiles along 
# with preparing all data.
source("d:/long_covid/scripts/functions/prep_redcap_data.R")
```


```{r}
#  Create a dataframe with binary variables to tabulate the number of screened, 
# enrolled, and consented patients.
tab_data <- data %>%
  select(
    record_id, enrollstatus, patient_consent_form_complete, healthrelated_social_needs_complete,
    participatingclinic, pcc_or_mdc_name) %>%
  group_by(record_id) %>%
  fill(
    enrollstatus, patient_consent_form_complete, healthrelated_social_needs_complete, 
    participatingclinic, pcc_or_mdc_name,  
    .direction = "updown") %>%
  slice_head() %>%
  ungroup() %>%
  # Convert missing values in enrollstatus to Unknown/ could be not yet screened or contacted but no response
  mutate(
    across(healthrelated_social_needs_complete, ~ ifelse(is.na(.x), "Unknown", .x))) %>%
  mutate(across(enrollstatus, ~ ifelse(is.na(.x), "TBD", .x))) %>%
  mutate(across(patient_consent_form_complete, ~ ifelse(is.na(.x), "Incomplete", .x)))
```

```{r}
#| eval: false

# What would study_label look like if tabulated
# data %>%
#   select(study_label) %>%
#   drop_na() %>%
#   tbl_summary()
```

# Referring clinic (pcc_or_mdc_name)
* Subsets to those that answered "Yes" to the question "Are you seeking care from a participating study clinic?"
* Variable implemented in mid-May 2026
```{r}
tab_data %>% 
  filter(participatingclinic == "Yes") %>%
  select(pcc_or_mdc_name) %>%
  tbl_summary()
```

# Screened and consented patients
- Total unique patients: Total number of unique record ids excluding test and duplicated records found in RedCap.
```{r}
tab_data %>%
  select(-record_id, -healthrelated_social_needs_complete) %>%
  # select(enrollstatus) %>%
  tbl_summary(
    label = list(
      enrollstatus ~ "RedCap field: enrollstatus",
      patient_consent_form_complete ~ "RedCap field: patient consent form complete"
      )
  ) %>%
  modify_header(label = "**Total unique patients**")
```


# Consented patients by Site Type and Site Name
```{r}
# Denominator of those that have consented
data %>%
  group_by(record_id) %>%
  slice_head() %>%
  ungroup() %>%
  filter(record_id %in% (tab_data %>% filter(patient_consent_form_complete == 1 | patient_consent_form_complete == "Complete") %>% pull(record_id))) %>%
  select(site_type, site_name) %>%
  tbl_summary(
    label = list(
      site_type ~ "Site Type",
      site_name ~ "Site Name")
  )
```

```{r}
#| eval: false
# This is the second table that I think Isabella and Marissa were asking for on 05/05/2026
# Sent out 5/18/2026, need to confirm
tab_data %>%
  select(-healthrelated_social_needs_complete) %>%
  left_join(
    data %>% 
      filter(record_id %in% tab_data$record_id) %>%
      group_by(record_id) %>%
      slice_head() %>%
      ungroup() %>%
      select(record_id, site_name), by = "record_id") %>%
  select(-record_id, -patient_consent_form_complete) %>%
  tbl_summary(
    by = enrollstatus,
  ) %>%
  add_overall()
```

# Survey completion rates by time point
- denominator consists of unique records where patient_consent_form is complete 
```{r}
# Denominator is a complete pre-enrollment form
# T1 Numerator is a complete health related social needs form at consent_and_t1_sur_arm_1
# T2 Numerator is a complete Experiences with care at t2_survey_arm_1
# T3 Numerator is a complete Experiences with care at t3_survey_arm_1
# T4 Numerator is a complete Experiences with care at t4_survey_arm_1
# T5 Numerator is a complete health related social needs form at t5_survey_arm_1
```

```{r}
# denominator
# *** patient record_id 41 consented, but patient_enrollment_form_complete not
# complete at T1
# The patient consent form complete can be used because there are no values 
# where patient consent is complete and consent_name is missing
consented_ids <- 
  tab_data %>%
  filter(patient_consent_form_complete == "Complete") %>%
  pull(record_id)

# Create a table using the record_ids in denominator ids which are the
# participants that have a complete patient_enrollment_form this will give
# the proportion of individuals who have consented and submitted a T1 
# survey out of those recruited from the clinics to undergo screening.


# Get the days since T1 for all consented patients
days_since_t1 <- data %>%
  filter(record_id %in% consented_ids, redcap_event_name == "consent_and_t1_sur_arm_1") %>%
  select(record_id, healthrelated_social_needs_timestamp) %>%
  mutate(mutate(across(healthrelated_social_needs_timestamp, ~ as.Date(.x)))) %>%
  mutate(days_since_t1 = as.numeric(Sys.Date() - healthrelated_social_needs_timestamp)) %>%
  select(record_id, days_since_t1)
 

# Get the values of those with a missing PASC at T1, since it's the completion 
# of the PASC that triggers the T2 and subsequent surveys.
incomplete_t1_pasc <- data %>%
  filter(redcap_event_name == "consent_and_t1_sur_arm_1", pasc_symptoms_and_followup_questions_complete == "Incomplete") %>%
  select(record_id, pasc_symptoms_and_followup_questions_complete)

# Merge the days since T1 to all rows by record_id
data <- data %>%
  left_join(days_since_t1, by = "record_id")

# Create separate data frames for each time point
t1_rates <- data %>%
    filter(record_id %in% consented_ids, redcap_event_name == "consent_and_t1_sur_arm_1") %>%
    select(record_id, healthrelated_social_needs_complete) %>%
    rename(t1_status = healthrelated_social_needs_complete)
    

t2_rates <- data %>%
    filter(record_id %in% consented_ids, redcap_event_name == "t2_survey_arm_1") %>% 
    select(record_id, experiences_with_care_complete) %>%
    rename(t2_status = experiences_with_care_complete)


t3_rates <- data %>%
    filter(record_id %in% consented_ids, redcap_event_name == "t3_survey_arm_1") %>% 
    select(record_id, experiences_with_care_complete) %>%
    rename(t3_status = experiences_with_care_complete)


t4_rates <- data %>%
    filter(record_id %in% consented_ids, redcap_event_name == "t4_survey_arm_1") %>% 
    select(record_id, experiences_with_care_complete) %>%
    rename(t4_status = experiences_with_care_complete)

t5_rates <- data %>%
    filter(record_id %in% consented_ids, redcap_event_name == "t5_survey_arm_1") %>%
    select(record_id, healthrelated_social_needs_complete) %>%
    rename(t5_status = healthrelated_social_needs_complete)

rates <- 
  t1_rates %>%
  left_join(t2_rates, by = "record_id") %>%
  left_join(t3_rates, by = "record_id") %>%
  left_join(t4_rates, by = "record_id") %>%
  left_join(t5_rates, by = "record_id") %>%

  left_join(days_since_t1, by = "record_id") %>%
  # filter(record_id == 3) %>% # !!! Coment out after troubleshooting
  mutate(across(t2_status:t5_status, ~ ifelse(record_id %in% incomplete_t1_pasc$record_id, "Incomplete T1 PASC", .x))) %>%
  
  # If the value is missing AND the days since t1 is less than 90, then the 
  # paticipant isn't due for a T2 yet, they haven't been in the study for
  # long enough
  mutate(t2_status = ifelse(
    is.na(t2_status) & days_since_t1 < 90, "Not due for T2", t2_status)) %>%

  # If the value is missing and the days since the T1 is between 90 and 104, 
  # then the patient is within the time window allowed in RedCap to submit a
  # survey
  mutate(t2_status = ifelse(
      is.na(t2_status) & days_since_t1 >= 90 & days_since_t1 < 104, 
      "Incomplete (within window)", 
      t2_status)) %>%

  # If the value is missing OR "Incomplete" AND the days since T1 is then the
  # patient is outside of the window allowed in RedCap and the value is missing
  mutate(t2_status = ifelse(
    (is.na(t2_status) | t2_status == "Incomplete") & days_since_t1 >= 104, 
    "Incomplete (past window)", 
    t2_status)) %>%

  # Modify t3 status ----------------------------------------------------------
  # The same manipulation for t2 are repeated here but with t3
  mutate(t3_status = ifelse(
    is.na(t3_status) & days_since_t1 < 180, "Not due for T3", t3_status)) %>%

  mutate(t3_status = ifelse(
    is.na(t3_status) & days_since_t1 >= 180 & days_since_t1 < 194, 
    "Incomplete (within window)", 
    t3_status)) %>%

  mutate(t3_status = ifelse(
    (is.na(t3_status) | t3_status == "Incomplete") & days_since_t1 >= 194, 
    "Incomplete (past window)", 
    t3_status)) %>%
  
  # Modify t4 status ----------------------------------------------------------
  mutate(t4_status = ifelse(
    is.na(t4_status) & days_since_t1 < 270, "Not due for T4", t4_status)) %>%

  mutate(t4_status = ifelse(
  is.na(t4_status) & days_since_t1 >= 270 & days_since_t1 < 284, 
  "Incomplete (within window)", 
  t4_status)) %>%

  mutate(t4_status = ifelse(
    (is.na(t4_status) | t4_status == "Incomplete") & days_since_t1 >= 284, 
    "Incomplete (past window)", 
    t4_status)) %>%

  # Modify t5 status ----------------------------------------------------------
  mutate(t5_status = ifelse(
    is.na(t5_status) & days_since_t1 < 360, "Not due for T5", t5_status)) %>%
  
  mutate(t5_status = ifelse(
    is.na(t5_status) & days_since_t1 >= 360 & days_since_t1 < 374,
      "Incomplete (within window)",
      t5_status)) %>%

  mutate(t5_status = ifelse(
    (is.na(t5_status) | t5_status == "Incomplete") & days_since_t1 >= 374,
    "Incomplete(past window)",
    t5_status
  ))
```

```{r}
rates %>%
  select(-record_id, -days_since_t1) %>%
  tbl_summary()
```

```{r}
# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
# LEFT OFF HERE SOME PATIENTS LIKE RECORD IDS 34 AND 69 END UP WITH NEGATIVE 
# VALUES WITH THIS CODE THAT IS DESIGNED TO COUNT HOW LONG IT TAKES FROM INVITE
# TO SURVEY COMPLETION FOR THE POST-T1 SURVEYS.
# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!


# rates

# Need time timestamps for t2, t3, t4, and t5, when complete
times <- data %>%
  # Make t1, t2, t3, t4, and t5 timestamps
  filter(
    record_id %in% consented_ids, 
    !redcap_event_name %in% c("patient_preenrollm_arm_1", "screening_and_enro_arm_1") ) %>%
  select(record_id, redcap_event_name, all_of(data %>% select(ends_with("timestamp")) %>% names())) %>%
  mutate(across(patient_consent_form_timestamp:pasc_symptoms_only_t2_t4_timestamp, ~ as.Date(.x))) %>%

# write_csv(times, "./patient_survey/data/long_covid_pt_survey_timestamps_qa.csv")


  select(
    record_id,
    redcap_event_name,
    patient_consent_form_timestamp, # *** For ids 55,34,37, 11, and 20, the hrsn timestamp for t1 does not match the consent timestamp. Almost as if the 1st hrsn was left blank and then a subsequent hrsn was filled in.
    healthrelated_social_needs_timestamp, 
    experiences_with_care_timestamp) %>%
  mutate(across(patient_consent_form_timestamp:experiences_with_care_timestamp, ~ as.Date(.x))) %>%
  mutate(timestamp =
    coalesce(
      patient_consent_form_timestamp,
      healthrelated_social_needs_timestamp, 
      experiences_with_care_timestamp)) %>%
  select(-(patient_consent_form_timestamp:experiences_with_care_timestamp)) %>%
  group_by(record_id) %>%
  pivot_wider(names_from = "redcap_event_name", values_from = "timestamp") %>%
  ungroup() %>%
  mutate(
    time_to_t2 = t2_survey_arm_1 - consent_and_t1_sur_arm_1
)
```

```{r}
#| eval: false 

# Older version of displaying the data, the problem is that the experience with care complete column
# is the same name at each T2- T4 timepoint.
# To get the 
tab_t1_t2_rates <- 
  data %>%
  filter(record_id %in% consented_ids) %>%
  group_by(record_id) %>%
  fill(c(
    healthrelated_social_needs_complete, 
    healthrelated_social_needs_timestamp,
    pasc_symptoms_and_followup_questions_complete,
    experiences_with_care_complete,
    experiences_with_care_timestamp), 
    .direction = "updown") %>%
  mutate(across(c(
    healthrelated_social_needs_timestamp, 
    experiences_with_care_timestamp), ~ as.Date(.x))) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(days_since_t1 = 
    as.numeric(Sys.Date() - healthrelated_social_needs_timestamp)) %>%
  select(
    record_id,
    healthrelated_social_needs_complete, 
    pasc_symptoms_and_followup_questions_complete,
    experiences_with_care_complete,
    days_since_t1) %>%
  mutate(t2_status = ifelse(
    is.na(experiences_with_care_complete) & days_since_t1 < 90, 
    "Not due", 
    experiences_with_care_complete)) %>%
  mutate(t2_status = ifelse(
    is.na(experiences_with_care_complete) & is.na(t2_status) & days_since_t1 >= 90 & days_since_t1 < 135, 
    "Within window", 
    t2_status)) %>%
  mutate(t2_status = ifelse(
    pasc_symptoms_and_followup_questions_complete == "Incomplete", "Incomplete PASC", t2_status
  ))
```

```{r}
#| eval: false
# To get the patients that need a nudge for a followup
tab_t1_t2_rates %>%
  filter(t2_status == "Incomplete (within window)") %>%
  select(record_id, experiences_with_care_complete, t2_status)
```

```{r}
# There are two patients in tab_t1_t2_rates, record_ids 17 and 41 that have a partial completion of the T1 survey. Not sure if they will receive an invite for T2.
```

## Survey completion rates by Site Type
* Those with an Incomplete T1 PASC were not administered subsequent surveys because completion of the T1 triggers subsequent invites
* Incomplete (past window) indicates a participant that was invited so submit a survey, but did not do so within 14 days of the invite
* Incomplete (within windows) indicates a participant that was invited to submit a survey, but is still within 14 days of invite and is eligible to submit a survey.
* T1 = baseline 0d, T2= 90d (3m), T3= 180d (6m), t4 = 270d (9m)
```{r}
rates %>%
  left_join(
    data %>% filter(record_id %in% rates$record_id) %>% select(site_type, record_id) %>% distinct(),
    by = "record_id"
  ) %>%
  select(t1_status, t2_status, t3_status, t4_status, site_type) %>%
  tbl_summary(by = site_type)
```

<!-- # Patient Demographics -->
```{r}
# Manually inspect gender_other as free text
# Manually inspect patient_sexorient_descr as free text
```

```{r}
# Make a backup
data_full <- data
```

```{r}
# Patient age gender and sexual orientation
data <- 
  data %>%
  filter(redcap_event_name == "consent_and_t1_sur_arm_1") %>%
  filter(record_id %in% consented_ids) %>%
  # mutate(patient_age = sample(18:75, n(), replace = TRUE)) %>% # Fabricate data
  mutate(age_group = case_when(
                               patient_age >= 18 & patient_age < 35 ~ "18-34",
                               patient_age >= 35 & patient_age < 65 ~ "35-64",
                               patient_age >= 65 ~ "65+",
                               TRUE ~ NA_character_
                               ),
         age_group = factor(age_group, levels = c("18-34", "35-64", "65+"), ordered = TRUE)) #%>%
 
```

# Patient demographics & characteristics
## Age, gender, sexual orientation
```{r}
# Patient age, gender and sexual orientation
data %>%
  select(age_group, patient_gender, patient_sexorient) %>%
  tbl_summary(
    # statistic = list(all_continuous() ~ "{mean} ({sd})"),
    label = list(
      age_group ~ "Age group",
      patient_gender ~ "Gender",
      patient_sexorient ~ "Sexual orientation"
    )
    )
```

## Race & ethnicity
```{r}
# Patient race and ethnicity
data %>%
  select(patient_race___1:patient_race___7, patient_ethn) %>%
  mutate(across(patient_race___1:patient_race___7, ~ factor(.x, levels = c(0, 1)))) %>%
  tbl_summary(
    label = list(
      "patient_race___1" ~ "African American or Black",
      "patient_race___2" ~ "American Indian/Alaska Native.",
      "patient_race___3" ~ "Asian",
      "patient_race___4" ~ "Native Hawaiian/Other Pacific Islander",
      "patient_race___5" ~ "White",
      "patient_race___6" ~ "Other",
      "patient_race___7" ~ "Prefer not to answer",
      "patient_ethn" ~ "Hispanic"),
    value = list(patient_race___1 ~ "1",
                 patient_race___2 ~ "1",
                 patient_race___3 ~ "1",
                 patient_race___4 ~ "1",
                 patient_race___5 ~ "1",
                 patient_race___6 ~ "1",
                 patient_race___7 ~ "1")
  )
```

## Patient preferred language
```{r}
# Patient preferred language
data %>%
  select(patient_pref_lang) %>%
  tbl_summary(
    label = list("patient_pref_lang" ~ "Patient preferred lang.")
  )
```

## Patient insurance
```{r}
# Patient race and ethnicity
data %>%
  select(patient_insurance___1:patient_insurance___10) %>%
  mutate(across(everything(), ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(
    label = list(
      "patient_insurance___1" ~ "State market place",
      "patient_insurance___2" ~ "Employee provided",
      "patient_insurance___3" ~ "Medicaid",
      "patient_insurance___4" ~ "Medicare - Original Medicare",
      "patient_insurance___5" ~ "Medicare - Advantage Plan",
      "patient_insurance___6" ~ "Worker's Comp",
      "patient_insurance___7" ~ "Other",
      "patient_insurance___8" ~ "Self-pay",
      "patient_insurance___9" ~ "Uninsured",
      "patient_insurance___10" ~ "Prefer not to answer",
      "patient_insurance___11" ~ "Medigap",
      "patient_insurance___12" ~ "Medicare Part D"
    ),
    value = everything() ~ "1"
  )
```

## Patient education level
```{r}
# Patient education level
data %>%
  select(patient_school) %>%
  tbl_summary(
    label = list(patient_school ~ "Patient education level")
  )
```

## Patient marital status
```{r}
data %>%
  select(patient_marital) %>%
  tbl_summary(
    label = list(patient_marital ~ "Patient marital status")
  )
```

## Patient employment status pre- long COVID
```{r}
data %>%
  select(patient_employ___1:patient_employ___7) %>%
  mutate(across(everything(), ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(
    label = list(
      patient_employ___1 ~ "Employed Full-time",
      patient_employ___2 ~ "Employed Part-time",
      patient_employ___3 ~ "Unemployed",
      patient_employ___4 ~ "Disabled",
      patient_employ___5 ~ "Retired",
      patient_employ___6 ~ "Student",
      patient_employ___7 ~ "Other"
    ),
    value = everything() ~ "1"
  )
```

## Patient employment status current
```{r}
data %>%
  # mutate(across(patient_employ_2___1:patient_employ_2___7, ~ sample(0:1, n(), replace = TRUE))) %>% # Fabricate data
  select(patient_employ_2___1:patient_employ_2___7) %>%
  mutate(across(everything(), ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(
    label = list(
      patient_employ_2___1 ~ "Employed Full-time",
      patient_employ_2___2 ~ "Employed Part-time",
      patient_employ_2___3 ~ "Unemployed",
      patient_employ_2___4 ~ "Disabled",
      patient_employ_2___5 ~ "Retired",
      patient_employ_2___6 ~ "Student",
      patient_employ_2___7 ~ "Other"
      ),
    value = everything() ~ "1"
  )
```