---
title: "EHR SDOH C4168_T3 (Work in progress)"

date: "`r format(Sys.Date(), '%m-%d-%Y')`"

format: 
  docx:
    toc: true
    embed-resources: true
    reference-doc: "D:/custom-reference-doc.docx"

execute: 
  echo: false
---


```{r}
# /////////////////////////////////////////////////////////////////////////////
# Carlos Rodriguez, PhD. CU Anschutz Dept. of Family Medicine
# AHRQ Long COVID - sdoh
# /////////////////////////////////////////////////////////////////////////////
```

```{r, message=FALSE, warning=FALSE}
library(magrittr, include = "%<>%")
library(tidyverse)
library(gtsummary)
library(dfmtbx)
```

```{r}
# Load data
# data <- read_csv(file = "D:\\long_covid\\sdoh\\C3924_T3_SDOH_20250417_AHRQ.csv",
#   show_col_types = FALSE)
data <- read_csv(file = "D:\\long_covid\\sdoh\\data\\C4168_T3_SDOH_20251120.csv",
  show_col_types = FALSE)

# Load dictionary for question text to flowsheet name
labels <- read_csv(file = "D:\\long_covid\\sdoh\\data\\SOCIAL DRIVERS FLOWSHEET VALUE.csv",
  show_col_types = FALSE)

# Remove the following ID, since they only have 3 rows of data and all are missing
data <- data %>% 
  filter(arb_person_id != "UCD46708466326")
```

```{r}
# demographics_old <- read_csv(file = "D:\\long_covid\\sdoh\\data\\C4167_Table1_Demographics.csv",
#   show_col_types = FALSE)

demographics <- read_csv(file = "D:\\long_covid\\sdoh\\data\\C4279_Table1_Demographics_20260324.csv",
  show_col_types = FALSE)

# Filter demographics to participants available in the flowsheet data
demographics %<>%
  filter(Pt_MDC %in% data$arb_person_id)
```

```{r}
# convert dd/mm/yyyy to yyyy/mm/dd
data %<>%
  mutate(date = as.Date(observation_date, format = "%m/%d/%Y"))
```

<!-- OLD CODE TO DETERMINE LABELS -->
```{r}
#| eval: false

# labels %>% drop_na()

# labels %>%
#   # mutate(across(everything(), ~ sub("\\[.*", "", .x))) %>%
#   # mutate(across(everything(), ~ str_trim(.x, side = "right"))) %>%
#   mutate(across(`Row Name`, ~ str_replace_all(.x, " ", "_")))

# write_csv(labels, "D:\\long_covid\\sdoh\\SOCIAL DRIVERS FLOWSHEET VALUE.csv")
```

# Unique participants from flowsheet data
```{r}
data %>%
  summarise(n = n_distinct(arb_person_id)) %>%
  format_gt_tbl()
```

# Unique number of flowsheet row names (questions)
```{r}
data %>%
  summarise(n = n_distinct(flowsheet_row_name)) %>%
  format_gt_tbl()
```

```{r}
# Recode age and insurance
demographics %<>%
  mutate(Pt_Age = case_when(
    Pt_Age %in% c("21 to 25", "26 to 30", "31 to 35", "36 to 40") ~ "21 to 40",
    Pt_Age %in% c("41 to 45", "46 to 50", "51 to 55", "56 to 60") ~ "41 to 60",
    .default = "61 to 85"
  ))

demographics %<>%
  mutate(Pt_Insurance_type = case_when(
    Pt_Insurance_type %in% c("AETNA", "ANTHEM", "ANTHEM FEDERAL", "CIGNA", "CU ANTHEM EXCLUSIVE", "DENVER HEALTH", "GREAT WEST", "UCHEALTH ANTHEM", "UNITED") ~ "Commercial",
    Pt_Insurance_type %in% c("COLORADO MEDICAID") ~ "Medicaid",
    Pt_Insurance_type %in% c("MEDICARE", "UNITED MEDICARE") ~ "Medicare",
    .default = NA 
  ))
```

# Demographics of unique participants in flowsheet data
```{r}
demographics %>%
  select(Pt_Age, Pt_Sex, Pt_Gender, Pt_Ethnicity, Pt_Race, Pt_language, Pt_Insurance_type) %>%
  tbl_summary()
```

<!-- # Frequencies & proportions for flowsheet row names (questions) -->
```{r}
unique_qs <- data %>% distinct(flowsheet_row_name) %>% pull()
```

```{r}
# Create two wide format data frames
data_wide <- data %>%
  group_by(arb_person_id) %>%
  pivot_wider(names_from = flowsheet_row_name, values_from = VALUE) %>%
  ungroup()

data_wide_num <- data %>%
  group_by(arb_person_id) %>%
  pivot_wider(names_from = flowsheet_row_name, values_from = VALUE) %>%
  ungroup()
```

```{r}
# Prepare data
col_names <- names(data_wide)
col_names <- str_replace_all(col_names, " ", "_")
names(data_wide) <- col_names

names(data_wide_num) <- col_names

data %<>% as_tibble()
```

```{r}
# Recode numeric data to categorical for frequencies and proportions
data_wide %<>% 
  # mutate 97 and 98 as Patient unable to answer, and Patient declined
  mutate(across(c(R_FINANCIAL_RESOURCE_STRAIN_BASICS), ~ case_match(.x, 
    "1" ~ "Very hard",
    "2" ~ "Hard",
    "3" ~ "Somewhat hard",
    "4" ~ "Not very hard",
    "5" ~ "Not hard at all",
    .default = .x))) %>%
# AUDIT -----------------------------------------------------------------------
mutate(across(c(R_AUDIT_ALCOHOL_BINGE), ~ case_match(.x, 
    "1" ~ "Never",
    "2" ~ "Less than monthly",
    "3" ~ "Monthly",
    "4" ~ "Weekly",
    "5" ~ "Daily or almost",
    "98" ~ "Declined",
    "97" ~ "Unable",
    .default = .x))) %>%
mutate(across(c(R_AUDIT_ALCOHOL_STD_DRINKS), ~ case_match(.x, 
    "0" ~ "Patient does not drink",
    "1" ~ "1 or 2",
    "2" ~ "3 or 4",
    "3" ~ "5 or 6",
    .default = .x))) %>%
mutate(across(c(R_AUDIT_ALCOHOL_FREQUENCY), ~ case_match(.x, 
    "1" ~ "Never",
    "2" ~ "Monthly or less",
    "3" ~ "2-4 times a month",
    "4" ~ "2-4 times a week",
    "5" ~ "4 or more times a week",
    .default = .x))) %>%
# Social Connection and Isolation Panel ---------------------------------------
mutate(across(c(R_SOCIAL_CONNECTIONS_MARITAL_STATUS), ~ case_match(.x,
    "3" ~ "Married",
    "4" ~ "Widowed",
    "5" ~ "Divorced",
    "6" ~ "Separated",
    "7" ~ "Never married",
    "8" ~ "Living with partner",
    .default = .x))) %>%
mutate(
  across(c(R_SOCIAL_CONNECTIONS_PHONE, 
           R_SOCIAL_CONNECTIONS_GET_TOGETHER), ~ case_match(.x,
    "1" ~ "Never",
    "2" ~ "Once a week",
    "3" ~ "Twice a week",
    "4" ~ "Three times a week",
    "5" ~ "More than three times a week",
    .default = .x))) %>%
mutate(
  across(c(R_SOCIAL_CONNECTIONS_RELIGION, 
           R_SOCIAL_CONNECTIONS_CLUB_ATTENDANCE), ~ case_match(.x,
    "1" ~ "Never",
    "2" ~ "1 to 4 times per year",
    "3" ~ "More than 4 times per year",
    "97" ~ "Unknown",
    .default = .x))) %>%
mutate(
  across(c(R_SOCIAL_CONNECTIONS_CLUB_MEMBERSHIP), ~ case_match(.x,
    "1" ~ "Yes",
    "2" ~ "No",
    .default = .x))) %>%
# Children's Watch ------------------------------------------------------------
mutate(
  across(c("R_CHILDREN'S_HEALTHWATCH_HOUSING_HOMELESS", 
           "R_CHILDREN'S_HEALTHWATCH_HOUSING_MORTGAGE"), ~ case_match(.x,
    "1" ~ "Yes",
    "2" ~ "No",
    .default = .x))) %>%
# Health Related Social Needs Screening Tool ----------------------------------
mutate(
  across(c(R_FOOD_INSECURITY_WORRY, 
           R_FOOD_INSECURITY_ABILITY_TO_PAY), ~ case_match(.x,
    "1" ~ "Never true",
    "2" ~ "Sometimes true",
    "3" ~ "Often true",
    .default = .x))) %>%
mutate(
  across(c(R_TRANSPORTATION_DAILY_LIVING, 
           R_TRANSPORTATION_MEDICAL_APPT,
           R_AHC_HRSN_UTILITIES), ~ case_match(.x,
    "1" ~ "Yes",
    "2" ~ "No",
    .default = .x))) %>%
mutate(
  across(c(R_AHC_HRSN_UTILITIES), ~ case_match(.x,
    "3" ~ "Already shut off",
    .default = .x))) %>%
# Stress Anxious --------------------------------------------------------------
mutate(
  across(c(R_STRESS_ANXIOUS), ~ case_match(.x,
    "1" ~ "Not at all",
    "2" ~ "Only a little",
    "3" ~ "To some extent",
    "4" ~ "Rather much",
    "5" ~ "Very much",
    .default = .x)))
```

# Food, transportation, & utilities insecurities
```{r}
old_names <- data_wide %>%
  select(starts_with("R_FOOD"), starts_with("R_TRANSPORTATION"), R_AHC_HRSN_UTILITIES) %>%
  names()

new_names <- labels %>%
  filter(`Row Name` %in% old_names)

data_wide %>%
  select(starts_with("R_FOOD"), starts_with("R_TRANSPORTATION"), R_AHC_HRSN_UTILITIES) %>%
  mutate(across(everything(), ~ fct_na_value_to_level(.x, level = "Unknown"))) %>%
  mutate(across(1:2, ~ factor(.x, levels = c("Never true", "Sometimes true", "Often true", "Unknown")))) %>%
  tbl_summary(
    type = list(everything() ~ "categorical"),
    label = list(
      R_AHC_HRSN_UTILITIES = new_names$`Row Display Name`[1],
      R_FOOD_INSECURITY_ABILITY_TO_PAY = new_names$`Row Display Name`[2],
      R_FOOD_INSECURITY_WORRY = new_names$`Row Display Name`[3],
      R_TRANSPORTATION_DAILY_LIVING = new_names$`Row Display Name`[4],
      R_TRANSPORTATION_MEDICAL_APPT = new_names$`Row Display Name`[5]
    )
  ) %>% bold_labels()  %>% modify_header(label = "Item")
```

## Unmet needs for food, transportation,  or utilities
```{r}
# Unmet food related need
data_wide %<>%
  mutate(
    food1 = R_FOOD_INSECURITY_ABILITY_TO_PAY,
    food2 = R_FOOD_INSECURITY_WORRY) %>%
  mutate(across(food1:food2, ~ ifelse(.x %in% c("Often true", "Sometimes true"), 1 ,0))) %>%
  mutate(unmet_food = rowSums(across(food1:food2), na.rm = TRUE)) %>%
  mutate(unmet_food = ifelse(unmet_food > 0, 1, 0))

# Unmet transportation related need
data_wide %<>%
  mutate(
    transp1 = R_TRANSPORTATION_DAILY_LIVING,
    transp2 = R_TRANSPORTATION_MEDICAL_APPT) %>%
  mutate(across(transp1:transp2, ~ ifelse(.x == "Yes", 1 ,0))) %>%
  mutate(unmet_transp = rowSums(across(transp1:transp2), na.rm = TRUE)) %>%
  mutate(unmet_transp = ifelse(unmet_transp > 0, 1, 0))


# Unmet utilities need
data_wide %<>%
  mutate(unmet_util = ifelse(R_AHC_HRSN_UTILITIES == "Yes", 1, 0)) %>%
  mutate(across(unmet_util, ~ ifelse(is.na(.x), 0, .x)))
```

```{r}
data_wide %>%
  select(unmet_food, unmet_transp, unmet_util) %>%
  tbl_summary()
```

# Housing insecurity (Children's health watch instrument)
```{r}
old_names <- data_wide %>%
  select(starts_with("R_CHILDREN")) %>%
  names()

new_names <- labels %>%
  filter(`Row Name` %in% old_names)

data_wide %>%
  select(starts_with("R_CHILDREN")) %>%
  mutate(across(everything(), ~ fct_na_value_to_level(.x, level = "Unknown"))) %>%
  tbl_summary(
    type = everything() ~ "categorical",
    label = list(
      `R_CHILDREN'S_HEALTHWATCH_HOUSING_HOMELESS` = new_names$`Row Display Name`[1],
      `R_CHILDREN'S_HEALTHWATCH_HOUSING_MORTGAGE` = new_names$`Row Display Name`[2],
      `R_CHILDREN'S_HEALTHWATCH_HOUSING_TIMES_MOVED` = "In the past 12 months, how many times have you moved where you were living?"
    )
  ) %>% bold_labels() %>% modify_header(label = "Item")
```  

```{r}
# Unmet housing need from Children's Healthwatch Survey
data_wide %<>%
  # select(starts_with("R_CHILDREN")) %>%
  mutate(
    chw1 = ifelse(as.numeric(`R_CHILDREN'S_HEALTHWATCH_HOUSING_TIMES_MOVED`) >= 2, 1, 0),
    chw2 = ifelse(`R_CHILDREN'S_HEALTHWATCH_HOUSING_MORTGAGE` == "Yes", 1, 0),
    chw3 = ifelse(`R_CHILDREN'S_HEALTHWATCH_HOUSING_HOMELESS` == "Yes", 1, 0)) %>%
  mutate(unmet_housing = rowSums(across(chw1:chw3))) %>%
  mutate(unmet_housing = ifelse(unmet_housing > 0, 1, 0)) %>%
  mutate(unmet_housing = ifelse(is.na(unmet_housing), 0, unmet_housing))
```

```{r}
data_wide %>%
  select(unmet_housing) %>%
  tbl_summary()
```

# Exercise
```{r}
data_wide %>%
  select(R_EXERCISE_DAYS_PER_WEEK, R_EXERCISE_MINUTES_PER_DAY) %>%
  # mutate(R_EXERCISE_MINUTES_PER_DAY = factor(as.numeric(R_EXERCISE_MINUTES_PER_DAY))) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  tbl_summary(
    # type = list(everything() ~ "categorical"),
    type = list(everything() ~ "continuous"),
    label = list(
      R_EXERCISE_DAYS_PER_WEEK = "On average, how many days per week do you engage in moderate to strenuous exercise (like a brisk walk)?",
      R_EXERCISE_MINUTES_PER_DAY = "On average, how many minutes do you engage in exercise at this level?"),
    statistic = list(everything() ~ "{mean} ({sd}; [{min}, {median}, {max}])")
  ) %>% bold_labels()
```

## Lack of physical activity (<= 150 minuts of exercise per week)
```{r}
### Less than 150 minutes of moderate or strenuous exercise per week
exercise <- data_wide %>%
  select(R_EXERCISE_DAYS_PER_WEEK, R_EXERCISE_MINUTES_PER_DAY) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  mutate(R_EXERCISE_MINUTES_PER_DAY = ifelse(R_EXERCISE_DAYS_PER_WEEK == 0, 0, R_EXERCISE_DAYS_PER_WEEK)) %>%
  mutate(minutes_exer_per_wk = R_EXERCISE_DAYS_PER_WEEK * R_EXERCISE_MINUTES_PER_DAY) %>%
  mutate(less_than_150m_per_wk = ifelse(minutes_exer_per_wk <= 150, 1, 0)) %>%
  mutate(less_than_150m_per_wk = ifelse(is.na(less_than_150m_per_wk), 0, less_than_150m_per_wk))
```

```{r}
#| eval: true
exercise %>%
  select(less_than_150m_per_wk) %>%
  tbl_summary(
    value = everything() ~ 1
  )
```

# Social Connections Isolation Panel
```{r}
old_names <- data_wide %>%
  select(starts_with("R_SOCIAL")) %>%
  names()

new_names <- labels %>%
  filter(`Row Name` %in% old_names)

data_wide %>%
  select(starts_with("R_SOCIAL")) %>%
  mutate(across(c(R_SOCIAL_CONNECTIONS_PHONE, R_SOCIAL_CONNECTIONS_GET_TOGETHER), ~ factor(.x, levels = c(
    "Never",
    "Once a week",
    "Twice a week",
    "Three times a week",
    "More than three times a week"
  )))) %>%
  mutate(R_SOCIAL_CONNECTIONS_MARITAL_STATUS = factor(R_SOCIAL_CONNECTIONS_MARITAL_STATUS, levels = c(
    "Married",
    "Widowed",
    "Divorced",
    "Separated",
    "Never married",
    "Living with partner"))) %>%
  mutate(across(everything(), ~ fct_na_value_to_level(.x, level = "Unknown"))) %>%
  tbl_summary(
    type = everything() ~ "categorical",
    label = list(
      R_SOCIAL_CONNECTIONS_CLUB_ATTENDANCE = new_names$`Row Display Name`[1],
      R_SOCIAL_CONNECTIONS_CLUB_MEMBERSHIP = new_names$`Row Display Name`[2],
      R_SOCIAL_CONNECTIONS_GET_TOGETHER = new_names$`Row Display Name`[3],
      R_SOCIAL_CONNECTIONS_MARITAL_STATUS = new_names$`Row Display Name`[4],
      R_SOCIAL_CONNECTIONS_PHONE = new_names$`Row Display Name`[5],
      R_SOCIAL_CONNECTIONS_RELIGION = new_names$`Row Display Name`[6]
    )
  )  %>% bold_labels() %>% modify_header(label = "Item")
```


```{r}
### Meets criteria for socially isolated
# https://loinc.org/76512-3
# Social isolation scores range from 0 to 4, with 0 representing the highest
# level of social isolation and 4 representing the lowest level. Scores of 0 or
# 1 are the most socially isolated participants. Patients received 1 point for
# each of the following: being married or living together with someone in a
# partnership at the time of questioning, averaging 3 or more interactions per
#  week with other people (assessed with the questions "In a typical week, how
# many times do you talk on the telephone with family, friends, or neighbors?"
# and "How often do you get together with friends or relatives?"), attending
# church or religious services 4 or more times per year, and reporting that they
# participate in a club or organization such as a church group, union, fraternal
# or athletic group, or school group. PMID: 24028260

isolation <- data_wide %>%
  select(starts_with("R_SOCIAL")) %>%
  mutate(
    R_SOCIAL_CONNECTIONS_MARITAL_STATUS = case_when(
      R_SOCIAL_CONNECTIONS_MARITAL_STATUS %in% c("Married", "Living with partner") ~ 1,
      .default = 0)) %>%
  mutate(across(c("R_SOCIAL_CONNECTIONS_GET_TOGETHER", "R_SOCIAL_CONNECTIONS_PHONE"), 
    ~ case_when(
      .x %in% c("Three times a week", "More than three times a week") ~ 1,
      .default = 0))) %>%
  mutate(across(c("R_SOCIAL_CONNECTIONS_RELIGION", "R_SOCIAL_CONNECTIONS_CLUB_ATTENDANCE"), 
    ~ case_when(
      .x %in% c("More than 4 times per year") ~ 1, 
      .default = 0))) %>%
  mutate(across(R_SOCIAL_CONNECTIONS_CLUB_MEMBERSHIP, ~ case_when(.x == "Yes" ~ 1, .default = 0)))

isolation %<>%
  mutate(social_iso_score1 = rowSums(across(everything()))) %>%
  mutate(socially_isolated1 = ifelse(social_iso_score1 <= 1, 1, 0))

isolation %<>%
  mutate(social_iso_score2 = rowSums(across(
    c("R_SOCIAL_CONNECTIONS_MARITAL_STATUS", "R_SOCIAL_CONNECTIONS_GET_TOGETHER", "R_SOCIAL_CONNECTIONS_PHONE", "R_SOCIAL_CONNECTIONS_RELIGION", "R_SOCIAL_CONNECTIONS_CLUB_MEMBERSHIP")
  ))) %>%
  mutate(socially_isolated2 = ifelse(social_iso_score2 <= 1, 1, 0))


```

## Scoring version 1
* EPIC data contains 6 items referencing social isolation. NHANES scoring guide for the social isolation panel references 5 out of the 6 questions.
* This version scores all 6 questions
* https://loinc.org/76512-3
```{r}
#| eval: true
isolation  %>%
  select(socially_isolated1) %>%
  tbl_summary()
```

## Scoring version 2
* Score only the 5 items referenced in the scoring guide.
```{r}
isolation  %>%
  select(socially_isolated2) %>%
  tbl_summary()
```

<!-- ## Custom scoring -->
```{r}
#| eval: false
isolation_jun <- data_wide %>%
  select(starts_with("R_SOCIAL")) %>%  
  mutate(across(c("R_SOCIAL_CONNECTIONS_GET_TOGETHER", "R_SOCIAL_CONNECTIONS_PHONE"), 
    ~ case_when(
      .x %in% c("Never", "Once a week") ~ 1,
      .default = 0))) %>%
  mutate(across(c("R_SOCIAL_CONNECTIONS_RELIGION", "R_SOCIAL_CONNECTIONS_CLUB_ATTENDANCE"), 
    ~ case_when(
      .x %in% c("Never") ~ 1, 
      .default = 0))) %>%
  mutate(across(R_SOCIAL_CONNECTIONS_CLUB_MEMBERSHIP, ~ case_when(.x == "No" ~ 1, .default = 0))) %>%
  mutate(R_SOCIAL_CONNECTIONS_MARITAL_STATUS = case_when(
    R_SOCIAL_CONNECTIONS_MARITAL_STATUS %in% c("Widowed", "Separated", "Never married") ~ 1,
      .default = 0)) %>%
  mutate(any_social_need = rowSums(across(everything()))) %>%
  mutate(any_social_need = ifelse(any_social_need >= 1, 1, 0)) 


isolation_jun %>%
  select(
    # R_SOCIAL_CONNECTIONS_GET_TOGETHER,
    # R_SOCIAL_CONNECTIONS_CLUB_MEMBERSHIP,
    # R_SOCIAL_CONNECTIONS_RELIGION,
    # R_SOCIAL_CONNECTIONS_CLUB_ATTENDANCE,
    # R_SOCIAL_CONNECTIONS_PHONE,
    # R_SOCIAL_CONNECTIONS_MARITAL_STATUS,
    any_social_need) %>%
  tbl_summary(
    label = any_social_need ~ "socially_isolated"
  )
```

# Occupational Stress Questionnaire (OSQ)
* https://loinc.org/76542-0
```{r}
# Occupational Stress Questionnaire Item
# https://loinc.org/76542-0
# https://pubmed.ncbi.nlm.nih.gov/14712852/
# https://www.sjweh.fi/article/752
# 2nd paragraph on pg. 445
# Any one in "rather much" through "very much" is a positive score
data_wide %<>%
  mutate(R_STRESS_ANXIOUS = factor(R_STRESS_ANXIOUS, levels = c(
    "Not at all",
    "Only a little",
    "To some extent",
    "Rather much",
    "Very much"))) %>%
  mutate(
    across(
      R_STRESS_ANXIOUS, ~ fct_na_value_to_level(.x, level = "Unknown")))
```

```{r}
data_wide %>% 
  select(R_STRESS_ANXIOUS) %>%
  tbl_summary(
    label = list(
      R_STRESS_ANXIOUS = "Do you feel stress, tense, restless, nervous, or anxious, or unable to sleep at night because your mind is troubled all the time - these days?"
    )
  ) %>% bold_labels %>% modify_header(label = "Item")
```

## Positive OSQ
```{r}
#  https://www.sjweh.fi/article/752
# 2nd paragraph on pg. 445
# Any one in "to some extent" through "very much" is a positive score *** need to double check this
data_wide %<>%
  mutate(osq_pos = ifelse(
    R_STRESS_ANXIOUS %in% c(
    # "To some extent", 
    "Rather much", 
    "Very much"), 1, 0))
```

```{r}
data_wide %>%
  select(osq_pos) %>%
  tbl_summary(
    # label = osq_pos ~ "stressed"
  )
```


# AUDI
* https://www.hepatitis.va.gov/alcohol/treatment/audit-c.asp
```{r}
old_names <- data_wide %>%
  select(starts_with("R_AUDIT")) %>%
  names()

new_names <- labels %>%
  filter(`Row Name` %in% old_names)

data_wide %>%
  # These questions are numbered Q1 through Q3 in the following order
  select(R_AUDIT_ALCOHOL_FREQUENCY, R_AUDIT_ALCOHOL_STD_DRINKS, R_AUDIT_ALCOHOL_BINGE) %>%
  mutate(R_AUDIT_ALCOHOL_FREQUENCY = factor(R_AUDIT_ALCOHOL_FREQUENCY,
    levels = c("Never",
    "Monthly or less",
    "2-4 times a month",
    "2-4 times a week",
    "4 or more times a week"))) %>%
  mutate(across(everything(), ~ fct_na_value_to_level(.x, level = "Unknown"))) %>%
  tbl_summary(
    type = list(everything() ~ "categorical"),
    label = list(
      R_AUDIT_ALCOHOL_BINGE = "How often do you have six or more drinks on one occasion?",
      R_AUDIT_ALCOHOL_FREQUENCY = "How often do you have a drink containing alcohol?",
      R_AUDIT_ALCOHOL_STD_DRINKS  = "How many drinks containing alcohol do you have on a typical day when you are drinking?"
    )
  ) %>% bold_labels %>% modify_header(label = "Item")
```

```{r}
# Score the Audit for AUD
# The numeric responses do not match up with the mapping needed to score.
# The numeric responses from COMPASS use a sequence of numeric values from 1 to
# 5, but the scoring requires a numeric value from 0 to 4. Values are 
# harmonized below.
# https://www.hepatitis.va.gov/alcohol/treatment/audit-c.asp

### AUDIT meets positive score
# * sex dependent scoring, 4 for men, 3 for women according

# Sex dependent scoring
# https://www.mdcalc.com/calc/2021/audit-c-alcohol-use#next-steps

# Set a global cutoff
cutoff <- 3

audit_num <- data_wide_num %>%
  # These questions are numbered Q1 through Q3 in the following order
  select(R_AUDIT_ALCOHOL_FREQUENCY, R_AUDIT_ALCOHOL_STD_DRINKS, R_AUDIT_ALCOHOL_BINGE) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  mutate(R_AUDIT_ALCOHOL_FREQUENCY = R_AUDIT_ALCOHOL_FREQUENCY - 1) %>%
  mutate(across(R_AUDIT_ALCOHOL_STD_DRINKS, ~ ifelse(.x == "1", 0, .x))) %>%
  mutate(R_AUDIT_ALCOHOL_BINGE = R_AUDIT_ALCOHOL_BINGE - 1) %>%
  mutate(audit_score = rowSums(across(everything()), na.rm = TRUE)) %>%
  mutate(all_vals_from_q1 = ifelse(audit_score == R_AUDIT_ALCOHOL_FREQUENCY, 1, 0)) %>%
  mutate(audit_pos = ifelse(audit_score >= cutoff, 1, 0)) %>%
  mutate(audit_pos = ifelse(all_vals_from_q1 == 1 & audit_pos == 1, 0, audit_pos))

# It does not matter if we use a global or sex dependent scoring system, when
# we adjust for all values from Q1. It also does not matter if the cutoff is
# set to 3 or 4, since some of these are modified by Q1
  # mutate(arb_person_id = data_wide$arb_person_id) %>%
  # left_join(., demographics %>% select(Pt_MDC, Pt_Sex), by = c("arb_person_id" = "Pt_MDC")) %>%
  # mutate(audit_pos = 0) %>%
  # mutate(audit_pos = ifelse(Pt_Sex == "male" & audit_score >= 4, 1, audit_pos)) %>% 
  # mutate(audit_pos = ifelse(Pt_Sex == "female" & audit_score >=3, 1, audit_pos)) %>%
  # mutate(audit_pos = ifelse(Pt_Sex == "unknown", NA, audit_pos)) %>%
  # mutate(across(audit_pos, ~ ifelse(is.na(.x), 0, .x)))
```

## National HIV curriculum scoring 
* Global summed score of 3 for all is set as the cut off. Additionally, sets the summed score to 0 if all points come from the Q1: "How often do you have a drink containing alcohol?"
* Other scoring systems do not adjust if all points come from the Q1. Others score according to sex, 3 as a cutoff for females and 4 for males.
```{r}
#| eval: false
# Preview table
audit_num %>%
  select(audit_pos) %>%
  tbl_summary()
```

<!-- ## Custom scoring -->
```{r}
#| eval: false
audit_jun <- data_wide %>%
  # These questions are numbered Q1 through Q3 in the following order
  select(R_AUDIT_ALCOHOL_FREQUENCY, R_AUDIT_ALCOHOL_STD_DRINKS, R_AUDIT_ALCOHOL_BINGE) %>%
  mutate(R_AUDIT_ALCOHOL_FREQUENCY = ifelse(R_AUDIT_ALCOHOL_FREQUENCY %in% c("2-4 times a week", "4 or more times a a weel"), 1 , 0 )) %>%
  mutate(R_AUDIT_ALCOHOL_STD_DRINKS = ifelse(R_AUDIT_ALCOHOL_STD_DRINKS %in% c("3 or 4", "5 or 6"), 1 ,0)) %>%
  mutate(R_AUDIT_ALCOHOL_BINGE = ifelse(R_AUDIT_ALCOHOL_BINGE %in% c("Less than monthly", "Weekly"), 1 ,0)) %>%
  mutate(audit_score = rowSums(across(everything()), na.rm = TRUE)) %>%
  mutate(audit_pos = ifelse(audit_score >= 1, 1, 0))

audit_jun %>%
  select(audit_pos) %>%
  tbl_summary()
```

# Health Literacy
```{r}
data_wide %<>%
  mutate(R_PAC_B1300 = factor(R_PAC_B1300, levels = c(
    "Never",
    "Rarely",
    "Sometimes",
    "Often",
    "Always"))) %>%
  mutate(
    across(
      R_PAC_B1300, ~ fct_na_value_to_level(.x, level = "Unknown"))) 
```

```{r}   
data_wide %>%
  select(R_PAC_B1300) %>%
  tbl_summary(
    label = list(
      R_PAC_B1300 = "How often do you need to have someone help you when you read instructions, pamphlets, or other written material from your doctor or pharmacy?"
    )
  ) %>% bold_labels %>% modify_header(label = "Item")
```

## Health literacy need
```{r}
# Health literacy
data_wide %<>%
  mutate(health_lit_pos = ifelse(R_PAC_B1300 %in% c("Often", "Always"), 1, 0))
```

```{r}
data_wide %>%
  select(health_lit_pos) %>%
  tbl_summary()
```

# Summary Table: All dichotomized domains
```{r}
summary_tab <- bind_cols(
    # Housing, food, transp, util, osq, health literacy
    data_wide %>%
      left_join(demographics, by = c("arb_person_id" = "Pt_MDC")) %>%
      select(Pt_Sex, Pt_Gender, Pt_Age, Pt_Race, unmet_food, unmet_transp, unmet_housing, unmet_util, osq_pos, health_lit_pos,),
    
    # exercise
    exercise %>%
      select(less_than_150m_per_wk),

    # social
    isolation  %>%
      select(socially_isolated1, socially_isolated2),

    # isolation_jun %>%
    #   select(any_social_need) %>%
    #   rename(socially_isolated2 = any_social_need),

    # AUDIT
    audit_num %>%
      select(audit_pos)

    # audit_jun %>%
    #   select(audit_pos) %>%
    #   rename(audit_pos2 = audit_pos)

)
```

```{r}
disp_labels <- list(
    # any_unmet_need ~ "Any unmet need",
    unmet_housing ~ "Unmet housing need",
    unmet_food ~ "Unmet food need",
    unmet_transp ~ "Unmet transportation need",
    unmet_util ~ "Unmet utility need",
    osq_pos ~ "Moderate to severely stressed",
    health_lit_pos ~ "Health literacy need",
    less_than_150m_per_wk ~ "Physical activity need",
    socially_isolated ~ "Social need",
    audit_pos ~ "Positive AUDIT-C")

summary_tab %>%
  select(-starts_with("Pt_")) %>%
  tbl_summary(
  # label = disp_labels,
  value = list(less_than_150m_per_wk ~ "1")
  )
```




<!-- WORKING BELOW HERE -->
<!-- ## Unmet Needs by Patient Characteristics -->
<!-- ### Sex -->
```{r}
#| eval: true
summary_tab %>%
  select(unmet_housing, unmet_food, unmet_transp, unmet_util, osq_pos, health_lit_pos, less_than_150m_per_wk,
  socially_isolated1, audit_pos, Pt_Sex) %>%
  mutate(across(starts_with("unmet"), ~ ifelse(is.na(.x), 0, .x))) %>%
  tbl_summary(
    by = Pt_Sex,
    # label = disp_labels,
    value = list(less_than_150m_per_wk ~ 1)
) %>% add_p()
```

```{r}
summary_tab %>%
  select(unmet_housing, unmet_food, unmet_transp, unmet_util, osq_pos, health_lit_pos, less_than_150m_per_wk,
  socially_isolated1, audit_pos, Pt_Gender) %>%
  mutate(across(starts_with("unmet"), ~ ifelse(is.na(.x), 0, .x))) %>%
  tbl_summary(
    by = Pt_Gender,
    # label = disp_labels,
    value = list(less_than_150m_per_wk ~ 1)
) %>% add_p()
```

```{r}
# add gender
# provide p-vals, for this and all other, just overall F test or chi square,

```

<!-- ### Age -->
```{r}
#| eval: true
summary_tab %>%
  select(unmet_housing, unmet_food, unmet_transp, unmet_util, osq_pos, health_lit_pos, less_than_150m_per_wk,
  socially_isolated1, audit_pos, Pt_Age) %>%
  mutate(across(starts_with("unmet"), ~ ifelse(is.na(.x), 0, .x))) %>%
  tbl_summary(
    by = Pt_Age,
    # label = disp_labels,
    value = list(less_than_150m_per_wk ~ 1)
) %>% add_p()
```

<!-- ### Race -->
```{r}
#| eval: true
summary_tab %>%
  mutate(Pt_Race = ifelse(Pt_Race == "white", "white", "non-white")) %>%
  select(unmet_housing, unmet_food, unmet_transp, unmet_util, osq_pos, health_lit_pos, less_than_150m_per_wk,
  socially_isolated1, audit_pos, Pt_Race) %>%
  mutate(across(starts_with("unmet"), ~ ifelse(is.na(.x), 0, .x))) %>%
  tbl_summary(
    by = Pt_Race,
    # label = disp_labels,
    value = list(less_than_150m_per_wk ~ 1)
  ) %>% add_p()
```
