---
title: "Employee Survey (draft)"

date: "`r format(Sys.Date(), '%m-%d-%Y')`"

format: 
  html:
    toc: true
    embed-resources: true

execute: 
  echo: false
---

```{r}
# /////////////////////////////////////////////////////////////////////////////
# Carlos Rodriguez, PhD. CU Anschutz Dept. of Family Medicine
# AHRQ Long COVID - employee survey
# /////////////////////////////////////////////////////////////////////////////
```

```{r, message=FALSE, warning=FALSE}
library(magrittr, include = "%<>%")
library(dfmtbx)

pacman::p_load(
  tidyverse,
  gtsummary
)
```

```{r, message=FALSE, warning=FALSE}
data <- pull_redcap_report(Sys.getenv("LC_employee"), "162831", "label", "raw")
data_numeric <- pull_redcap_report(Sys.getenv("LC_employee"), "162831", "raw", "raw")
labels <- pull_redcap_report(Sys.getenv("LC_employee"), "162831", "label", "label")
```

```{r}
# Create a field-name to label-name dictionary given two data frames in the 
# workspace named labels and data, where data is the report pulled from Redcap
# in raw format and labels is the same report but with the label format.
create_name_dict <- function(){
  # create a dictionary
  dict <- data.frame( 
  field_name = names(data), 
  label = names(labels))

  return(dict)
}
```

```{r}
# FUNCTION TO CONVERT CHECKED/UNCHECKED COLUMNS TO 1/0
check_to_binary <- function (df, cols = everything(), val_to_1 = "Checked") {
  df %>%
    mutate(across({{cols}}, ~ map_int(.x, ~ ifelse(.x == val_to_1, 1, 0))))
}
```

```{r}
# Function that converts a raw header to a label header, requires th dict
# data frame to be present in the workspace
raw_to_label_header <-  function(df) {

  temp <- df

  current_names <- names(df)
  
  new_names <- dict %>% 
    filter(field_name %in% current_names) %>% 
    pull(label)
  
  names(temp) <- new_names

  return(temp)

}
```

```{r}
# Function to convert Unkowns to Missing
```

```{r}
# Create the label header dictionary
dict <- create_name_dict()
```

```{r}
test <- 
  data %>%
    select(consent_name, employee_survey_t1_complete)
```


# Consent rate
- Denominator is the total number of records available in Redcap
```{r}
data %>%
  mutate(consented = if_else(is.na(consent_name), 0, 1)) %>%
  select(consented) %>%
  tbl_summary()
```

```{r}
# Drop those that have not consented to participate
data %<>%
  filter(!is.na(consent_name))
```



# Completion rate
* Denominator is the number of people that provided consent
```{r}
data %>%
  select(employee_survey_t1_complete) %>%
  tbl_summary()
```

```{r}
data %<>%
  filter(employee_survey_t1_complete == "Complete")
```

```{r}
# filter data_numeric in the same way that data_raw is filtered
data_numeric %<>%
  filter(record_id %in% data$record_id)
```

<!-- Data processing -->
```{r}
# Recode pcc_or_mdc to MDC or PCC
data %<>%
  mutate(pcc_or_mdc = case_match(
    pcc_or_mdc,
    "practice" ~ "PCC",
    "clinic" ~ "MDC",
    .default = NA
  ))

data_numeric %<>%
  mutate(pcc_or_mdc = case_match(
    pcc_or_mdc,
    1 ~ "PCC",
    2 ~ "MDC",
    .default = NA
  ))

# Create a categorical version of years of experience
data %<>%
  mutate(experience_cat = cut(experience, 
   breaks =  c(-Inf, 1, 5, 10, Inf),
   labels = c("<=1", "2-5", "6-10", ">10")))
```

# Demographics
- subset of only those that completed
```{r}
#| eval: false
data %>%
  select(gender:personal_covid, experience_cat) %>%
  select(-fte, -experience) %>% #omit fte until further processing
  tbl_summary()
```

```{r}
# Demographics by site type
data %>%
  select(gender:personal_covid, experience_cat, pcc_or_mdc) %>%
  select(-fte, -experience) %>% #omit fte until further processing
  # mutate(pcc_or_mdc = ifelse(pcc_or_mdc == "clinic", "MDC", "PCC")) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  tbl_summary(
    by = pcc_or_mdc) %>%
  add_overall()
```

# Practice role PCC
```{r}
data %>%
  filter(pcc_or_mdc == "PCC") %>%
  select(practice_role_pcc) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  tbl_summary()
```

# To what extent do you agree with this statement: "Treatment and symptom management for patients with Long COVID is something that a primary care practice should provide to their patients as part of comprehensive primary care." Select one number. (PCC only)
```{r}
data %>%
  filter(pcc_or_mdc == "PCC") %>%
  select(agree_statement_pcc) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  tbl_summary()
```

```{r}
data_numeric %>%
  filter(pcc_or_mdc == "PCC") %>%
  select(agree_statement_pcc) %>%
  tbl_summary(
    type = list(agree_statement_pcc ~ "continuous"),
    statistic = all_continuous() ~ c("{mean} ({sd}); {median} ({p25}, {p75})"),
    missing = "no"
  )
```


# Practice role MDC
```{r}
data %>%
  filter(pcc_or_mdc == "MDC") %>%
  select(practice_role_mdc) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  tbl_summary()
```

# Specialty MDC
```{r}
data %>%
  filter(pcc_or_mdc == "MDC") %>%
  select(specialty_mdc) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  tbl_summary()
```


# How satisfied are you with this [pcc_or_mdc]'s ability to help patients manage their Long COVID symptoms? Select the one best answer.
```{r}
data %>%
  # mutate(pcc_or_mdc = ifelse(pcc_or_mdc == "clinic", "MDC", "PCC")) %>%
  select(help_manage, pcc_or_mdc) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  tbl_summary(by = pcc_or_mdc) %>%
  add_overall()
```

# What are your concerns about starting/providing Long COVID treatment at this practice? Select all that apply (PCC only)
```{r}
data %>%
  filter(pcc_or_mdc == "PCC") %>%
  select(starts_with("starting_treatment_pcc")) %>%
  mutate(across(everything(), ~ifelse(.x == "Checked", 1, 0))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c(0, 1)))) %>%
  tbl_summary(
    label = list(
      starting_treatment_pcc___1 ~ "I/our providers don't have time in their schedule",
      starting_treatment_pcc___2 ~ "We won't get paid / will lose money",
      starting_treatment_pcc___3 ~ "I/our providers don't know how",
      starting_treatment_pcc___4 ~ "I/our providers don't feel like patients will be able to successfully manage symptoms",
      starting_treatment_pcc___5 ~ "I/our providers are not interested in providing Long COVID treatment",
      starting_treatment_pcc___6 ~ "We don't have Long COVID treatment workflows set up in our practice",
      starting_treatment_pcc___7 ~ "We don't have time to set up a new program",
      starting_treatment_pcc___8 ~ "Our providers don't have the ancillary rehab supports needed to treat the condition (e.g. PT, OT, etc.)",
      starting_treatment_pcc___9 ~ "Other",
      starting_treatment_pcc___10 ~ "None of the above are concerns"),
    value = list(starting_treatment_pcc___1 ~ "1",
                 starting_treatment_pcc___2 ~ "1",
                 starting_treatment_pcc___3 ~ "1",
                 starting_treatment_pcc___4 ~ "1",
                 starting_treatment_pcc___5 ~ "1",
                 starting_treatment_pcc___6 ~ "1",
                 starting_treatment_pcc___7 ~ "1",
                 starting_treatment_pcc___8 ~ "1",
                 starting_treatment_pcc___9 ~ "1",
                 starting_treatment_pcc___10 ~ "1")
  )
```

# The following items assess the climate for managing Long COVID symptoms in this [pcc_or_mdc]. Please select one number for each item listed below.
```{r}
#| eval: false
# tbl_summary version
data %>%
  select(expect_certain_number:appreciation, pcc_or_mdc) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  tbl_summary(by = pcc_or_mdc) %>%
  add_overall()
```

## Numeric scores
```{r}
ic_scores <- data_numeric %>%
    select(expect_certain_number:appreciation, record_id) %>%
    score_ic_scale(., "record_id")
```

```{r}
data %<>%
  left_join(ic_scores, by = "record_id")
```

```{r}
data %>%
  select(AvgImplScale, pcc_or_mdc) %>%
  tbl_summary(by = pcc_or_mdc,
    type = all_continuous() ~ "continuous",
    statistic = all_continuous() ~ c("{mean} ({sd}); {median} ({p25}, {p75}))")
  ) %>%
  add_overall()
```


## Overall
```{r}
# tbl_likert version
data %>%
  select(expect_certain_number:appreciation) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  raw_to_label_header() %>%
  mutate(across(everything(), ~ factor(.x, levels = c(
    "1 - Not at all",
    "2",
    "3 - Somewhat",
    "4",
    "5 - To a Great Extent",
    "Unknown"
  )))) %>%
  tbl_likert()
```


## PCC
```{r}
data %>%
  filter(pcc_or_mdc == "PCC") %>%
  select(expect_certain_number:appreciation) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  raw_to_label_header() %>%
  mutate(across(everything(), ~ factor(.x, levels = c(
    "1 - Not at all",
    "2",
    "3 - Somewhat",
    "4",
    "5 - To a Great Extent",
    "Unknown"
  )))) %>%
  tbl_likert()
```

## MDC
```{r}
data %>%
  filter(pcc_or_mdc == "MDC") %>%
  select(expect_certain_number:appreciation) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  raw_to_label_header() %>%
  mutate(across(everything(), ~ factor(.x, levels = c(
    "1 - Not at all",
    "2",
    "3 - Somewhat",
    "4",
    "5 - To a Great Extent",
    "Unknown"
  )))) %>%
  tbl_likert()
```

# Confidence and effectiveness
* Subset to physician and APP at PCC or Physician, Resident, APP at MDC
```{r}
data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") | 
    practice_role_mdc %in% c("Physician", "Resident physician/Fellow", "Certified nurse specialist, nurse practitioner, or advanced practice nurse", "Physician assistant")) %>%
  select(confidence:effective) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  tbl_summary()
```


```{r}
ids <- data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") | 
    practice_role_mdc %in% c("Physician", "Resident physician/Fellow", "Certified nurse specialist, nurse practitioner, or advanced practice nurse", "Physician assistant")) %>%
  pull(record_id)

data_numeric %>%
  filter(record_id %in% ids) %>%
  select(confidence:effective) %>%
  tbl_summary(
    type = list(everything() ~ "continuous"),
        statistic = all_continuous() ~ c("{mean} ({sd}); {median} ({p25}, {p75})"),
    missing = "no"
  )
```

# Have you gotten additional CME on how to provide treatment for Long COVID?
* Subset to physician and APP at PCC or Physician, Resident, APP at MDC
```{r}
data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") | 
    practice_role_mdc %in% c("Physician", "Resident physician/Fellow", "Certified nurse specialist, nurse practitioner, or advanced practice nurse", "Physician assistant")) %>%
  select(additional_cme) %>%
  tbl_summary()
```

# To what extent do you provide these services for patients with Long COVID? Please check one box for each item listed below.  
* Subset to physician and APP at PCC or Physician, Resident, APP at MDC
```{r}
#| eval: false
data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") | 
    practice_role_mdc %in% c("Physician", "Resident physician/Fellow", "Certified nurse specialist, nurse practitioner, or advanced practice nurse", "Physician assistant")) %>%
  select(identify_patients:other_service_matrix) %>%
  tbl_summary()
```

```{r}
data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") | 
    practice_role_mdc %in% c("Physician", "Resident physician/Fellow", "Certified nurse specialist, nurse practitioner, or advanced practice nurse", "Physician assistant")) %>%
  select(identify_patients:other_service_matrix) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  raw_to_label_header() %>%
  mutate(across(everything(), ~ factor(.x, levels = c(
    "Not at All",
    "Sometimes",
    "Very Often",
    "Unknown"
  )))) %>%
  tbl_likert() %>%
  add_n()
```

# I am not involved in any of the items listed above
* Subset to physician and APP at PCC or Physician, Resident, APP at MDC
```{r}
data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") | 
    practice_role_mdc %in% c("Physician", "Resident physician/Fellow", "Certified nurse specialist, nurse practitioner, or advanced practice nurse", "Physician assistant")) %>%
  select(not_involved___1) %>%
  raw_to_label_header() %>%
  check_to_binary() %>%
  tbl_summary()
```


# Which of the following would you be interested in learning more about? Select all that apply
* Subset to PCC Physician or APP
```{r}
data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") ) %>%
  select(starts_with("interest_learning_pcc")) %>%
  mutate(across(everything(), ~ifelse(.x == "Checked", 1, 0))) %>%
  tbl_summary(
    label = list(
      interest_learning_pcc___1 ~ "How to prescribe/appropriate medications for Long COVID symptoms",
      interest_learning_pcc___2 ~ "Therapeutic alternatives",
      interest_learning_pcc___3 ~ "How to organize workflows to accommodate Long COVID patients",
      interest_learning_pcc___4 ~ "Options for how to organize Long COVID management in a busy practice",
      interest_learning_pcc___5 ~ "Recommendations around specific treatment options, as well as which ones work and do not work",
      interest_learning_pcc___6 ~ "	Helping patients who are struggling with ongoing symptoms",
      interest_learning_pcc___7 ~ "Resources to refer patients to for symptom treatment and management",
      interest_learning_pcc___8 ~ "	Apps, tools and other materials to use with patients with Long COVID",
      interest_learning_pcc___9 ~ "	How to bill for/get paid for Long COVID visits",
      interest_learning_pcc___10 ~ "How to organize and track Long COVID symptoms with patients over time in the EMR",
      interest_learning_pcc___11 ~ "Other",
      interest_learning_pcc_no___1 ~ "I am not interested in any of these options listed above"
    )
  )
```

# In which of the following ways would you like to learn? Rank each item in order of your preference, with number 1 as the most preferred way to learn, to number 8 as the least preferred way to learn.
* Subset to PCC Physician or APP
```{r}
#| eval: false
data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") ) %>%
  select(elearning_module_pcc:uptodate_pcc) %>%
  tbl_summary()
```

```{r}
data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") ) %>%
  select(elearning_module_pcc:uptodate_pcc) %>%
  mutate(referral_system_pcc = as.character(referral_system_pcc)) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  raw_to_label_header() %>%
  mutate(across(everything(), ~ factor(.x, levels = c(
    "1 - Most preferred",
    "2",
    "3",
    "4",
    "5",
    "6",
    "7",
    "8 - Least preferred",
    "Unknown"
  )))) %>%
  tbl_likert() %>%
  add_n()
```


### Lower = more preferred
```{r}
ids <- data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") ) %>%
  pull(record_id)


data_numeric %>%
  filter(record_id %in% ids) %>%
  select(elearning_module_pcc:uptodate_pcc) %>%
  raw_to_label_header() %>%
  tbl_summary(
    type = everything() ~ "continuous",
    statistic = all_continuous() ~ c("{mean} ({sd}); {median} ({p25}, {p75})"),
    missing = "no"
  )
```


## I would not like to learn in any of these ways
```{r}
data %>%
  filter(
    practice_role_pcc %in% c("Physician", "Advanced practice provider (NP, PA)") ) %>%
  select(not_like_to_learn_pcc___1) %>%
  check_to_binary() %>%
  tbl_summary()
```

# Culture
* For each of the following questions, please indicate your level of agreement or disagreement with each statement as it applies to this [pcc_or_mdc] overall, not just for Long COVID care. For each item, select one item on the scale ranging from strongly disagree to strongly agree. 1 = strongly disagree (SD), 2 = disagree (D), 3 = neither agree nor disagree (N), 4 = agree (A), 5 = strongly agree (SA)

```{r}
pc_scores <- data_numeric %>%
  select(record_id, after_change:environment) %>%
  score_pc_scale(., "record_id")
```

```{r}
# Merge the scored practice culture values with the main data frame
data %<>%
  left_join(., pc_scores, by = "record_id")
```

## Numeric scores
```{r}
data %>%
  select(pc_imp_subscore:CultureAvg, pcc_or_mdc) %>%
  tbl_summary(by = pcc_or_mdc,
    type = everything() ~ "continuous",
    statistic = all_continuous() ~ c("{mean} ({sd}); {median} ({p25}, {p75})")
  ) %>%
  add_overall()
```

## Overall frequencies
```{r}
data %>%
  select(after_change:environment) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c("SD (1)", "D (2)", "N (3)", "A (4)", "SA (5)", "Unknown")))) %>%
  raw_to_label_header() %>%
  tbl_likert() %>%
  add_n()
```

## PCC frequencies
```{r}
data %>%
  filter(pcc_or_mdc == "PCC") %>%
  select(after_change:environment) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c("SD (1)", "D (2)", "N (3)", "A (4)", "SA (5)" ,"Unknown")))) %>%
  raw_to_label_header() %>%
  tbl_likert() %>%
  add_n()
```

## MDC frequencies
```{r}
data %>%
  filter(pcc_or_mdc == "MDC") %>%
  select(after_change:environment) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c("SD (1)", "D (2)", "N (3)", "A (4)", "SA (5)", "Unknown")))) %>%
  raw_to_label_header() %>%
  tbl_likert() %>%
  add_n()
```

# Please answer the following questions regarding patients with Long COVID symptoms (choose one number for each item) 1 = strongly disagree (SD), 2 = disagree (D), 3 = neither agree nor disagree (N), 4 = agree (A), 5 = strongly agree (SA)

## Overall
```{r}
data %>%
  select(prefer_not:waste_dollars) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c("SD (1)", "D (2)", "N (3)", "A (4)", "SA (5)", "Unknown")))) %>%
  raw_to_label_header() %>%
  tbl_likert() %>%
  add_n()
```


## PCC
```{r}
data %>%
  filter(pcc_or_mdc == "PCC") %>%
  select(prefer_not:waste_dollars) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c("SD (1)", "D (2)", "N (3)", "A (4)", "SA (5)" ,"Unknown")))) %>%
  raw_to_label_header() %>%
  tbl_likert() %>%
  add_n()
```

## MDC
```{r}
data %>%
  filter(pcc_or_mdc == "MDC") %>%
  select(prefer_not:waste_dollars) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c("SD (1)", "D (2)", "N (3)", "A (4)", "SA (5)", "Unknown")))) %>%
  raw_to_label_header() %>%
  tbl_likert() %>%
  add_n()
```

# Using your own definition of "burnout," please indicate which statement best describes your situation working at this [pcc_or_mdc] overall, not just for Long COVID care. Check one box:
```{r}
data %>%
  select(burnout_situation, pcc_or_mdc) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(burnout_situation = factor(burnout_situation, levels = c(
    "I enjoy my work. I have no symptoms of burnout.",
    "Occasionally I am under stress, and I don't always have as much energy as I once did, but I don't feel burned out.",
    "I am definitely burning out and have one or more symptoms of burnout, such as physical and emotional exhaustion.",
    "The symptoms of burnout that I'm experiencing won't go away. I think about frustrations at work a lot.",
    "I feel completely burned out and often wonder if I can go on. I am at the point where I may need some changes or may need to seek some sort of help.",
    "Prefer not to answer",
    "Unknown"
  ))) %>%
  tbl_summary(by = pcc_or_mdc) %>%
  add_overall()
```

# Please answer these questions about your work satisfaction. 1 = strongly disagree (SD), 2 = disagree (D), 3 = neither agree nor disagree (N), 4 = agree (A), 5 = strongly agree (SA)

## Overall
```{r}
data %>%
  select(rewarding, satisfied) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c("SD (1)", "D (2)", "N (3)", "A (4)", "SA (5)", "Unknown")))) %>%
  raw_to_label_header() %>%
  tbl_likert() %>%
  add_n()
```

## PCC
```{r}
data %>%
  filter(pcc_or_mdc == "PCC") %>%
  select(rewarding, satisfied) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c("SD (1)", "D (2)", "N (3)", "A (4)", "SA (5)", "Unknown")))) %>%
  raw_to_label_header() %>%
  tbl_likert() %>%
  add_n()
```

## MDC
```{r}
data %>%
  filter(pcc_or_mdc == "MDC") %>%
  select(rewarding, satisfied) %>%
  mutate(across(everything(), ~ if_else(is.na(.x), "Unknown", .x))) %>%
  mutate(across(everything(), ~ factor(.x, levels = c("SD (1)", "D (2)", "N (3)", "A (4)", "SA (5)", "Unkown")))) %>%
  raw_to_label_header() %>%
  tbl_likert() %>%
  add_n()
```