---
title: "AHRQ Long COVID - Patient Survey Results by Timepoint"

date: "`r format(Sys.Date(), '%m-%d-%Y')`"

format: 
  docx:
    toc: true
    embed-resources: true
    reference-doc: "D:/custom-reference-doc.docx"

execute: 
  echo: false
---

```{r}
# -----------------------------------------------------------------------------
# Carlos Rodriguez, PhD. CU Dept. of Family Medicine
# 01-12-2026

# Prep Longitudinal Data

# Description - This script is designed to download, prep and clean the RedCap
# data from the AHRQ Long COVID project.

# This script is part 2 of 2 in a series of code files that produce reports
# for the patient survey data.This file specifically displays out any 
# information by time point when available.


# -----------------------------------------------------------------------------
```

```{r, message=FALSE, warning=FALSE}
library(magrittr, include = "%<>%")

library(dfmtbx)
# renv::install("carlosivanr/dfmtbx") # To update

library(tidyverse)
library(gtsummary)
```

```{r}
# Run the prep longitudinal data script
# source("D:\\long_covid\\patient_survey\\prep_longitudinal_data.R")

source("d:/long_covid/scripts/functions/prep_redcap_data.R")

```

```{r}
t1 <- data %>% filter(timepoint == 1) %>% filter(!is.na(consent_name))

t2 <- data %>% filter(timepoint == 2) %>% filter(!is.na(consent_name))
```

# Patient demographics & characteristics
## Age, gender, sexual orientation
```{r}
# Patient age, gender and sexual orientation
t1 %>%
  select(age_group, patient_gender, patient_sexorient) %>%
  tbl_summary(
    # statistic = list(all_continuous() ~ "{mean} ({sd})"),
    label = list(
      age_group ~ "Age group",
      patient_gender ~ "Gender",
      patient_sexorient ~ "Sexual orientation"
    )
    )
```

## Race & ethnicity
```{r}
# Patient race and ethnicity
t1 %>%
  select(patient_race___1:patient_race___7, patient_ethn) %>%
  mutate(across(patient_race___1:patient_race___7, ~ factor(.x, levels = c(0, 1)))) %>%
  tbl_summary(
    label = list(
      "patient_race___1" ~ "African American or Black",
      "patient_race___2" ~ "American Indian/Alaska Native.",
      "patient_race___3" ~ "Asian",
      "patient_race___4" ~ "Native Hawaiian/Other Pacific Islander",
      "patient_race___5" ~ "White",
      "patient_race___6" ~ "Other",
      "patient_race___7" ~ "Prefer not to answer",
      "patient_ethn" ~ "Hispanic"),
    value = list(patient_race___1 ~ "1",
                 patient_race___2 ~ "1",
                 patient_race___3 ~ "1",
                 patient_race___4 ~ "1",
                 patient_race___5 ~ "1",
                 patient_race___6 ~ "1",
                 patient_race___7 ~ "1")
  )
```

## Patient preferred language
```{r}
# Patient preferred language
t1 %>%
  select(patient_pref_lang) %>%
  tbl_summary(
    label = list("patient_pref_lang" ~ "Patient preferred lang.")
  )
```

## Patient insurance
```{r}
# Patient race and ethnicity
t1 %>%
  select(patient_insurance___1:patient_insurance___10) %>%
  mutate(across(everything(), ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(
    label = list(
      "patient_insurance___1" ~ "State market place",
      "patient_insurance___2" ~ "Employer provided",
      "patient_insurance___3" ~ "Medicaid",
      "patient_insurance___4" ~ "Medicare - Original Medicare",
      "patient_insurance___5" ~ "Medicare - Advantage Plan",
      "patient_insurance___6" ~ "Worker's Comp",
      "patient_insurance___7" ~ "Other",
      "patient_insurance___8" ~ "Self-pay",
      "patient_insurance___9" ~ "Uninsured",
      "patient_insurance___10" ~ "Prefer not to answer",
      "patient_insurance___11" ~ "Medigap",
      "patient_insurance___12" ~ "Medicare Part D"
    ),
    value = everything() ~ "1"
  )
```

## Patient education level
```{r}
# Patient education level
t1 %>%
  select(patient_school) %>%
  tbl_summary(
    label = list(patient_school ~ "Patient education level")
  )
```

## Patient marital status
```{r}
t1 %>%
  select(patient_marital) %>%
  tbl_summary(
    label = list(patient_marital ~ "Patient marital status")
  )
```

## Patient employment status pre- long COVID
```{r}
t1 %>%
  select(patient_employ___1:patient_employ___7) %>%
  mutate(across(everything(), ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(
    label = list(
      patient_employ___1 ~ "Employed Full-time",
      patient_employ___2 ~ "Employed Part-time",
      patient_employ___3 ~ "Unemployed",
      patient_employ___4 ~ "Disabled",
      patient_employ___5 ~ "Retired",
      patient_employ___6 ~ "Student",
      patient_employ___7 ~ "Other"
    ),
    value = everything() ~ "1"
  )
```

## Patient employment status current
```{r}
t1 %>%
  select(patient_employ_2___1:patient_employ_2___7) %>%
  mutate(across(everything(), ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(
    label = list(
      patient_employ_2___1 ~ "Employed Full-time",
      patient_employ_2___2 ~ "Employed Part-time",
      patient_employ_2___3 ~ "Unemployed",
      patient_employ_2___4 ~ "Disabled",
      patient_employ_2___5 ~ "Retired",
      patient_employ_2___6 ~ "Student",
      patient_employ_2___7 ~ "Other"
      ),
    value = everything() ~ "1"
  )
```

<!-- //////////// PATIENT CLINICAL QUESTIONS AT T1 AND T5 ONLY //////////// -->
# Patient clinical questions
* Currently subsets to those that provided consent.

## 	For how many months do you feel you have had Long COVID symptoms (regardless of formal diagnosis)? (For example, 1 year would be 12 months; 2 years would be 24 months; 3 years would be 36 months) 
```{r}
t1 %>%
  select(months_symps) %>%
  tbl_summary(
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  )
```


## Do you now have a diagnosis from a health care provider of Long COVID?
```{r}
t1 %>%
  select(lcdiagnosis) %>%
  tbl_summary()
```

### If yes, how many months did it take for you to get that diagnosis after your symptoms started? (For example, 1 year would be 12 months; 2 years would be 24 months; 3 years would be 36 months)
```{r}
t1 %>%
  filter(lcdiagnosis == 1) %>%
  select(
    ifyes_monthsymps) %>%
  tbl_summary(
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  )
```


## 	Which of the following conditions had you been diagnosed with prior to (before) developing Long COVID symptoms? (check all that apply)
```{r}
# Order the condition from most frequent to least frequent
ordered_conditions <- t1 %>% 
  select(conditions___1:conditions___14) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(cols = everything(), names_to = "condition", values_to = "count") %>%
  arrange(desc(count)) %>%
  pull(condition)
```

```{r}
t1 %>%
  select(conditions___1:conditions___14) %>%
  select(all_of(ordered_conditions)) %>%
  tbl_summary(
    label = list(
      "conditions___1" ~ "Hypertension",
      "conditions___2" ~ "Obesity",
      "conditions___3" ~ "Chronic lung disease (COPD, asthma, pulmonary fibrosis)",
      "conditions___4" ~ "Diabetes Mellitus",
      "conditions___5" ~ "Chronic immune suppression (organ transplant, HIV)",
      "conditions___6" ~ "Coronary artery disease",
      "conditions___7" ~ "High cholesterol",
      "conditions___8" ~ "Heart arrhythmias",
      "conditions___9" ~ "Major depression",
      "conditions___10" ~ "Anxiety",
      "conditions___11" ~ "PTSD",
      "conditions___12" ~ "Cancer",
      "conditions___13" ~ "Other (please describe)",
      "conditions___14" ~ "None"),
    value = everything() ~ "1"
  )
```

```{r}
# All who selected "Other" did not provide free text so far
# commented here 
other_condition_n <- t1 %>%
  filter(conditions___14 == 1) %>%
  select(conditions_other) %>%
  drop_na() %>%
  nrow()

if (other_condition_n >= 1) {
  t1 %>%
    filter(conditions___14 == 1) %>%
    select(conditions_other) %>%
    tbl_summary()
}
```

## Have you received or increased your dose of any of the following medications specifically for Long COVID or Long COVID symptoms? (select all that apply)
```{r}
# Order the medications from most frequent to least frequent
ordered_medications <- t1 %>% 
  select(medications___1:medications___13) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(cols = everything(), names_to = "medication", values_to = "count") %>%
  arrange(desc(count)) %>%
  pull(medication)
```

```{r}
t1 %>%
  select(medications___1:medications___13) %>%
  select(all_of(ordered_medications)) %>%  
  tbl_summary(
    label = list(
      "medications___1" ~ "Paxlovid",
      "medications___2" ~ "Low dose naltrexone",
      "medications___3" ~ "Heart rate controlling agents (beta-blockers, calcium channel blockers, ivabradine)",
      "medications___4" ~ "Prednisone",
      "medications___5" ~ "Lung inhaler medications (Symbicort, Advair/Wixela, Breo)",
      "medications___6" ~ "Midodrine",
      "medications___7" ~ "Fludricortisone",
      "medications___8" ~ "SSRIs/SNRIs",
      "medications___9" ~ "Memantine",
      "medications___10" ~ "Adderall/Ritalin",
      "medications___11" ~ "Modafinil",
      "medications___12" ~ "Other (please specify)",
      "medications___13" ~ "None"),
    value = everything() ~ "1"
  )
```

### Other medicine (please specify)
```{r}
# All who selected "Other" 
other_medication_n <- t1 %>%
  filter(medications___13 == 1) %>%
  select(other_med) %>%
  drop_na() %>%
  nrow()

if (other_medication_n >= 1) {
  t1 %>%
    filter(medications___13 == 1) %>%
    select(other_med) %>%
    tbl_summary()
}
```

## Have you received any of the following therapies specifically for Long COVID or Long COVID symptoms? (select all that apply)
```{r}
ordered_therapies <- t1 %>%
  select(therapies___13:therapies___21) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(cols = everything(), names_to = "therapy", values_to = "count") %>%
  arrange(desc(count)) %>%
  pull(therapy)
```

```{r}
t1 %>%
  select(therapies___13:therapies___21) %>%
  select(all_of(ordered_therapies)) %>%
  tbl_summary(
    label = list(
      "therapies___13" ~ "Speech therapy/cognitive training",
      "therapies___14" ~ "Physical therapy",
      "therapies___15" ~ "Occupational therapy",
      "therapies___16" ~ "Group therapy/peer support",
      "therapies___17" ~ "Pulmonary rehab",
      "therapies___18" ~ "Counseling/mental or behavioral health therapy",
      "therapies___19" ~ "Complementary/alternative therapies (examples like acupuncture, supplements, chiropractic, etc.)",
      "therapies___20" ~ "Other (please specify)",
      "therapies___21" ~ "None"),
    value = everything() ~ "1"
  )
```

## Other services (please specify)
```{r}
# All who selected "Other" 
other_therapies_n <- t1 %>%
  filter(therapies___20 == 1) %>%
  select(other_med) %>%
  drop_na() %>%
  nrow()

if (other_therapies_n >= 1) {
  t1 %>%
    filter(therapies___20 == 1) %>%
    select(other_service) %>%
    tbl_summary()
}
```

```{r}
# Filter out the pre-enrollment and screening timepoints
data %<>% filter(!is.na(timepoint))
```

# PROMIS Global Health
## Global physical and mental health subscores
* PROMIS physical health and mental health subscores range from 4 (min) - 20 (max) 
```{r}
data %>%
  select(promis_global_phys, promis_global_ment, redcap_event_name) %>%  
  tbl_summary(
    by = redcap_event_name,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      promis_global_phys ~ "Global physical health",
      promis_global_ment ~ "Global mental health"
    )
  )
```


## Promis Global Health Physical and Mental Health T-Scores
```{r}
# Display the tables of T-Score and their averages
data %>%
  select(promis_pht, promis_mht, redcap_event_name) %>%
  tbl_summary(
    by = redcap_event_name,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      promis_pht ~ "Global physical health T-score",
      promis_mht ~ "Global mental health T-score"
      # promis_global01 ~ "In general, would you say your health is:",
      # promis_global09r ~ "In general, please rate how well you carry out your usual social activities and roles."
    )
  )
```

## In general, would you say your health is:
```{r}
data %>%
  select(promis_1, redcap_event_name) %>%
  tbl_summary(
    by = redcap_event_name,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      # promis_global_phys ~ "Global physical health",
      # promis_global_ment ~ "Global mental health",
      # promis_global01 ~ "In general, would you say your health is:",
      # promis_global09r ~ "In general, please rate how well you carry out your usual social activities and roles."
    )
  )
```


## In general, please rate how well you carry out your usual social activities and roles.
```{r}
data %>%
  select(promis_9, redcap_event_name) %>%
  tbl_summary(
    by = redcap_event_name,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      # promis_global_phys ~ "Global physical health",
      # promis_global_ment ~ "Global mental health",
      # promis_global01 ~ "In general, would you say your health is:",
      # promis_global09r ~ "In general, please rate how well you carry out your usual social activities and roles."
    )
  )
```


# PASC
```{r}
data %>%
  # filter(timepoint %in% c(1,2,3,4,5)) %>%
  select(pasc_score, 
    pasc_positive, 
    redcap_event_name) %>%
  tbl_summary(
    by = redcap_event_name,
    statistic = list(pasc_score ~ "{mean} ({sd}); [{min}, {median}, {max}]"),
    value = list(pasc_positive ~ "1"))
```


# Experiences of Stigma
## Have you had one or more appointments with medical providers at a primary care clinic in the past three months?
```{r}
data %>%
  filter(timepoint %in% c(1,5)) %>%
  select(pcc_appts, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

```{r}
# data %>%
#   filter(timepoint %in% c(1,5)) %>%
#   select(pcc_appts, redcap_event_name) %>%
#   mutate(pcc_appts = ifelse(is.na(pcc_appts), "Unknown", pcc_appts)) %>%
#   tbl_summary(by = redcap_event_name)
```



## Mean score of "lack of understanding" scale from Illness Invalidation Inventory PCC
* n.b. Subsets to those that answered "Yes" to the question "Have you had one or more appointments with medical providers at a primary care clinic in the past three months?"
* Scale ranges from 1(min) to 5(max), with 1 indicating the lowest perceived understanding from medical providers and 5 indicated the highest perceived understanding.
* Only asked at T1 and T5
```{r}
# This should be two variables lack_understand_pcc, and lack_understand_mdc, and each is subset to "Yes" in appts_mdc or appts_pcc
data %>%
  filter(
    timepoint %in% c(1, 5), 
    pcc_appts == "Yes"
    ) %>%
  select(lou_score_pcc, redcap_event_name) %>%
  tbl_summary(
    by = redcap_event_name,
    type = everything() ~ "continuous",
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  )
```

<!-- INDIVIDUAL SCORES -->
## Individual questions: How often in the past 3 months did medical professionals at your primary care clinic react to you in the following ways:
### Medical professionals took me seriously.
```{r}
data %>%
  filter(pcc_appts == "Yes", (timepoint %in% c(1, 5))) %>%
  select(serious_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### Medical professionals understood the consequences of my health problems or illness.
```{r}
data %>%
  filter(pcc_appts == "Yes", (timepoint %in% c(1, 5))) %>%
  select(consequences_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### Medical professionals gave me the chance to talk about what is on my mind.
```{r}
data %>%
  filter(pcc_appts == "Yes", (timepoint %in% c(1, 5))) %>%
  select(talk_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

## Have you had one or more appointments with medical providers at a multi-disciplinary Long COVID clinic in the past three months?
```{r}
data %>%
  filter(timepoint %in% c(1,5)) %>%
  select(mdc_appts, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

## Mean score of "lack of understanding" scale from Illness Invalidation Inventory MDC
* n.b. Subsets to those that answered "Yes" to the question "Have you had one or more appointments with medical providers at a multi-disciplinary care clinic in the past three months?"
* Scale ranges from 1(min) to 5(max), with 1 indicating the lowest perceived understanding from medical providers and 5 indicated the highest perceived understanding.
* Only asked at T1 and T5
```{r}
# This should be two variables lack_understand_pcc, and lack_understand_mdc, and each is subset to "Yes" in appts_mdc or appts_pcc
data %>%
  filter(
    timepoint %in% c(1, 5), 
    mdc_appts == "Yes"
    ) %>%
  select(lou_score_mdc, redcap_event_name) %>%
  tbl_summary(
    by = redcap_event_name,
    type = everything() ~ "continuous",
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  )
```

## Individual questions: How often in the past 3 months did medical professionals at your primary care clinic react to you in the following ways:
### Medical professionals took me seriously.
```{r}
data %>%
  filter(mdc_appts == "Yes", (timepoint %in% c(1, 5))) %>%
  select(serious_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### Medical professionals understood the consequences of my health problems or illness.
```{r}
data %>%
  filter(mdc_appts == "Yes", (timepoint %in% c(1, 5))) %>%
  select(consequences_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### Medical professionals gave me the chance to talk about what is on my mind.
```{r}
data %>%
  filter(mdc_appts == "Yes", (timepoint %in% c(1, 5))) %>%
  select(talk_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

<!-- LEFT OFF HERE, NEED TO DISPLAY EVERYTHING BY TIME POINT -->
# Health Related Social Needs (t1 & t5 only)
## Living Situation
### What is your living situation today?
```{r}
data %>%
  filter(timepoint %in% c(1, 5)) %>%
  select(living_sit, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### Think about the place you live. Do you have problems with any of the following?
```{r}
data %>%
  filter(timepoint %in% c(1, 5)) %>%
  select(living_probs___1:living_probs___8, redcap_event_name) %>%
  tbl_summary(
    by = redcap_event_name,
    value = everything() ~ "1",
    label = list(
      living_probs___1 ~ "Pests such as bugs, ants, or mice",
      living_probs___2 ~ "Mold",
      living_probs___3 ~ "Lead paint or pipes",
      living_probs___4 ~ "Lack of heat",
      living_probs___5 ~ "Oven or stove not working",
      living_probs___6 ~ "Smoke detectors missing or not working",
      living_probs___7 ~ "Water leaks",
      living_probs___8 ~ "None of the above"
    )
  )
```

## Food
### Within the past 12 months, were you worried that your food would run out before you got money to buy more?
```{r}
data %>%
  filter(timepoint %in% c(1, 5)) %>%
  select(redcap_event_name, food_worry) %>%
  tbl_summary(by = redcap_event_name)
```

### Within the past 12 months, has the food you bought just didn't last and you didn't have money to get more?
```{r}
data %>%
  filter(timepoint %in% c(1, 5)) %>%
  select(redcap_event_name, food_last) %>%
  tbl_summary(by = redcap_event_name)
```

## Transportation
### In the past 12 months, has lack of reliable transportation kept you from medical appointments, meetings, work or from getting things needed for daily living?
```{r}
data %>%
  filter(timepoint %in% c(1, 5)) %>%
  select(redcap_event_name, transport) %>%
  tbl_summary( 
    by = redcap_event_name,
    type = list(transport ~ "categorical")
  )
```

## Utilities
### In the past 12 months has the electric, gas, oil, or water company threatened to shut off services in your home?
```{r}
data %>%
  filter(timepoint %in% c(1, 5)) %>%
  select(redcap_event_name, utlities) %>%
  tbl_summary(
    by = redcap_event_name,
    type = list(utlities ~ "categorical")
  )
```

## Financial Strain
### How hard is it for you to pay for the very basics like food, housing, medical care, and heating? Would you say it is:
```{r}
data %>%
  filter(timepoint %in% c(1, 5)) %>%
  select(redcap_event_name, fin_strain) %>%
  tbl_summary(
    by = redcap_event_name,
    type = list(fin_strain ~ "categorical")
  )
```

## Family & Community Support
### If for any reason you need help with day-to-day activities such as bathing, preparing meals, shopping, managing finances, etc., do you get the help you need?
```{r}
data %>%
  filter(timepoint %in% c(1, 5)) %>%
  select(redcap_event_name,help_daytoday) %>%
  mutate(help_daytoday = factor(help_daytoday, levels = c("I don't need any help", "I get all the help I need", "I could use a little more help", "I need a lot more help"))) %>%
  tbl_summary( 
    by = redcap_event_name,
    type = list(help_daytoday ~ "categorical")
  )
```

### How often do you feel lonely or isolated from those around you?
```{r}
data %>%
  filter(timepoint %in% c(1, 5)) %>%
  select(redcap_event_name, lonely) %>%
  mutate(lonely = factor(lonely, levels = c("Never", "Rarely", "Sometimes", "Often", "Always"))) %>%
  tbl_summary( 
  by = redcap_event_name,
    type = list(lonely ~ "categorical")
  )
```

## Summary of needs by domain
```{r}
hrsn_data %>%
  select(
    living_need,
    food_need,
    transport_need,
    utlities_need,
    fin_strain_need,
    social_need,
    hrsn_need_score,
    redcap_event_name) %>%
  mutate(across(living_need:social_need, ~ factor(.x, levels = c(1, 0)))) %>%
  tbl_summary(
    by = redcap_event_name,
    value = everything() ~ "1",
    missing = "no",
    type = list(hrsn_need_score ~ "continuous"),
    statistic = list(hrsn_need_score ~ "{mean}, ({sd}); [{min}, {median}, {max}]"),
    label = list(transport_need ~ "transportation_need", utlities_need ~ "utilities_need"))
```


# Experiences with care (t2 -t4 only)

## PCC
```{r}
# PCC questions
# data %<>%
#   mutate(across(c(explain_pcc:medinfo_pcc, helpful_pcc:courtesy_pcc), ~ factor(.x, levels = c(
#     "Yes, definitely",
#     "Yes, somewhat",
#     "No"))))

# data %<>%
#   mutate(across(test_pcc:results_pcc, ~ factor(.x, levels = "Yes", "No")))
```

### During your most recent visit, did this provider explain things in a way that was easy to understand?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_pcc == "Yes") %>%
  select(explain_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### During your most recent visit, did this provider listen carefully to you?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_pcc == "Yes") %>%
  select(listen_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### During your most recent visit, did this provider show respect for what you had to say?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_pcc == "Yes") %>%
  select(respect_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### During your most recent visit, did this provider spend enough time with you?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_pcc == "Yes") %>%
  select(time_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### During your most recent visit, did this provider have the medical information they needed about you?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_pcc == "Yes") %>%
  select(medinfo_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```


### During your most recent visit, did this provider order a blood test, x-ray, or other test for you?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_pcc == "Yes") %>%
  select(test_pcc, redcap_event_name) %>%
  tbl_summary(
    by = redcap_event_name,
    type = list(everything() ~ "categorical"))
```

### Did someone from this provider's office follow up to give you those results?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_pcc == "Yes") %>%
  select(results_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### Thinking about your most recent visit, was the staff from this provider's office as helpful as you thought they should be?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_pcc == "Yes") %>%
  select(helpful_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### Thinking about your most recent visit, did the staff from this provider's office treat you with courtesy and respect?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_pcc == "Yes") %>%
  select(courtesy_pcc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

## MDC
```{r}
# # MDC questions
# data %<>%
#   mutate(across(c(explain_mdc:medinfo_mdc, helpful_mdc:courtesy_mdc), ~ factor(.x, levels = c(
#     "Yes, definitely",
#     "Yes, somewhat",
#     "No"))))

# data %<>%
#   mutate(across(test_mdc:results_mdc, ~ factor(.x, levels = "Yes", "No")))
```

### During your most recent visit, did this provider explain things in a way that was easy to understand?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_mdc == "Yes") %>%
  select(explain_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### During your most recent visit, did this provider listen carefully to you?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_mdc == "Yes") %>%
  select(listen_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### During your most recent visit, did this provider show respect for what you had to say?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_mdc == "Yes") %>%
  select(respect_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### During your most recent visit, did this provider spend enough time with you?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_mdc == "Yes") %>%
  select(time_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### During your most recent visit, did this provider have the medical information they needed about you?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_mdc == "Yes") %>%
  select(medinfo_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```


### During your most recent visit, did this provider order a blood test, x-ray, or other test for you?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_mdc == "Yes") %>%
  select(test_mdc, redcap_event_name) %>%
  tbl_summary(
    by = redcap_event_name,
    type = list(everything() ~ "categorical"))
```

### Did someone from this provider's office follow up to give you those results?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_mdc == "Yes") %>%
  select(results_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### Thinking about your most recent visit, was the staff from this provider's office as helpful as you thought they should be?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_mdc == "Yes") %>%
  select(helpful_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```

### Thinking about your most recent visit, did the staff from this provider's office treat you with courtesy and respect?
```{r}
data %>%
  filter(timepoint %in% c(2, 3, 4), appt_mdc == "Yes") %>%
  select(courtesy_mdc, redcap_event_name) %>%
  tbl_summary(by = redcap_event_name)
```