---
title: "AHRQ Long COVID - T1 Patient Survey Results"

date: "`r format(Sys.Date(), '%m-%d-%Y')`"

format: 
  docx:
    toc: true
    embed-resources: true
    reference-doc: "D:/custom-reference-doc.docx"

execute: 
  echo: false
---


```{r}
# Carlos Rodriguez, PhD. CU Dept. of Family Medicine
# 01-15-2026

# Patient Survey Data by Site Type

# Description - This script is a branch from the original patient_survey.qmd 
# file that has been modified to display all of the survey questions by 
# site_type (MDC or PCC).
```


```{r, message=FALSE, warning=FALSE}
library(magrittr, include = "%<>%")

library(dfmtbx)
# renv::install("carlosivanr/dfmtbx") # To update

library(tidyverse)
library(gtsummary)
```

```{r}
#| echo: false
# Participant accrual report draft
# Project ID = 33298
# Report ID = 176060
```


```{r, message=FALSE, warning=FALSE}
# Pull report 176060 as labeled data
# Corresponds to patient_enrollment report in REDCap
data <- pull_redcap_report(Sys.getenv("LC_patient"), "176060", "label", "raw", "true")

# Capture the column names
names_data <- names(data)

# Drop the demographic select all that apply questions
data %<>%
  select(
    -starts_with("patient_race"),
    -starts_with("patient_insurance"),
    -starts_with("patient_employ"),
    -redcap_event_name # use raw instead of label to preserve prior functions
)
```

```{r, message=FALSE, warning=FALSE}
# Pull report 176060 as raw data for the demographic variables only
demographics <- 
  pull_redcap_report(Sys.getenv("LC_patient"), "176060", "raw", "raw", "false") %>%
  select(
    redcap_event_name,
    starts_with("patient_race"),
    starts_with("patient_insurance"),
    starts_with("patient_employ")
  )
```

```{r}
# Merge the primary data set with the demographic data set
data <- bind_cols(data, demographics)

# Re-order the columns to preserve the order in the the data frame data
data %<>%
  select(all_of(names_data))

# Rename promis_record_id to record_id (easier to type)
data %<>%
  rename(record_id = promis_record_id)

# Clear workspace variables
rm(demographics, names_data)
```


```{r}
# Identify test records as those with the "test" in the name field OR those
# with "test record" in the anything else field
# ids 14, 15, 16, and 18 flagged as test Ids. (CR 12/09/2025)
# ids, 64, 65 flagged as test ids. (CR 2/23/2026)
test_ids <-
  data %>%
    filter(
      grepl("test", name, ignore.case = TRUE) | 
      grepl("test record", anythingelse, ignore.case = TRUE) |
      grepl("test", study_label, ignore.case = TRUE)
      ) %>%
    pull(record_id)


# Identify duplicated record_ids as those with "Duplicated record" in the 
# enrollstatus field
# Ids 10, 35, 36, 38, flagged as duplicate Ids
# Id 69 flagged as duplicate (02/23/2026)
duplicated_ids <- 
  data %>%
    filter(
      grepl("duplicate", enrollstatus, ignore.case = TRUE) |
      grepl("duplicate", study_label, ignore.case = TRUE)
      ) %>%
    pull(record_id)

# Remove the test and duplicated ids
data %<>%
  filter(!record_id %in% c(test_ids, duplicated_ids))
```


```{r}
# /////////////////////////////// Data Clean Up ///////////////////////////////
# Create a site variable by coalescing mdc_name and pcc_name before filling
# values
data %<>%
  mutate(site_name = coalesce(mdc_name, pcc_name))

# Fill in empty values for pcc_or_mdc, mdc_name, and pcc_name columns
data %<>%
  group_by(record_id) %>%
  fill(pcc_or_mdc, .direction = c("updown")) %>%
  fill(site_name, .direction = c("updown")) %>%
  ungroup()

# Rename pcc_or_mdc to site_type for readability, and make unknown explicit
data %<>%
  rename(site_type = pcc_or_mdc) %>%
  mutate(site_type = ifelse(is.na(site_type), "Unknown", site_type)) %>%
  mutate(site_name = ifelse(is.na(site_name), "Unknown", site_name))
```

```{r}
#  Create a dataframe consisting of those that have consented
tab_data <- data %>%
  select(record_id, enrollstatus, patient_consent_form_complete, healthrelated_social_needs_complete) %>%
  group_by(record_id) %>%
  fill(enrollstatus, patient_consent_form_complete, healthrelated_social_needs_complete, .direction = "updown") %>%
  slice_head() %>%
  ungroup() %>%
  # Convert missing values in enrollstatus to Unknown/ could be not yet screened or contacted but no response
  mutate(
    across(enrollstatus:healthrelated_social_needs_complete, ~ ifelse(is.na(.x), "Unknown", .x))) %>%
  filter(patient_consent_form_complete == 1 | patient_consent_form_complete == "Complete")
```


```{r}
t1 <- data %>% filter(record_id %in% tab_data$record_id, redcap_event_name == "consent_and_t1_sur_arm_1")
t2 <- data %>% filter(record_id %in% tab_data$record_id, redcap_event_name == "t2_survey_arm_1")
```

# Patient demographics & characteristics
```{r}
# Patient age gender and sexual orientation
t1 %<>%
  mutate(age_group = case_when(
                               patient_age >= 18 & patient_age < 35 ~ "18-34",
                               patient_age >= 35 & patient_age < 65 ~ "35-64",
                               patient_age >= 65 ~ "65+",
                               TRUE ~ NA_character_
                               ),
         age_group = factor(age_group, levels = c("18-34", "35-64", "65+"), ordered = TRUE))
 
```

## Age, gender, sexual orientation
```{r}
# Patient age, gender and sexual orientation
t1 %>%
  select(site_type, age_group, patient_gender, patient_sexorient) %>%
  tbl_summary(
    by = site_type,
    # statistic = list(all_continuous() ~ "{mean} ({sd})"),
    label = list(
      age_group ~ "Age group",
      patient_gender ~ "Gender",
      patient_sexorient ~ "Sexual orientation"
    )
    ) %>%
    add_overall() %>% add_p()
```

## Race & ethnicity
```{r}
# Patient race and ethnicity
t1 %>%
  select(site_type, patient_race___1:patient_race___7, patient_ethn) %>%
  mutate(across(patient_race___1:patient_race___7, ~ factor(.x, levels = c(0, 1)))) %>%
  tbl_summary(
    by = site_type,
    label = list(
      "patient_race___1" ~ "African American or Black",
      "patient_race___2" ~ "American Indian/Alaska Native.",
      "patient_race___3" ~ "Asian",
      "patient_race___4" ~ "Native Hawaiian/Other Pacific Islander",
      "patient_race___5" ~ "White",
      "patient_race___6" ~ "Other",
      "patient_race___7" ~ "Prefer not to answer",
      "patient_ethn" ~ "Hispanic"),
    value = list(patient_race___1 ~ "1",
                 patient_race___2 ~ "1",
                 patient_race___3 ~ "1",
                 patient_race___4 ~ "1",
                 patient_race___5 ~ "1",
                 patient_race___6 ~ "1",
                 patient_race___7 ~ "1")
  ) %>%
    add_overall() %>% add_p()
```

## Patient preferred language
```{r}
# Patient preferred language
t1 %>%
  select(site_type, patient_pref_lang) %>%
  tbl_summary(by = site_type,
    label = list("patient_pref_lang" ~ "Patient preferred lang.")
  ) %>%
    add_overall()
```

## Patient insurance
```{r}
# Patient race and ethnicity
t1 %>%
  select(site_type, patient_insurance___1:patient_insurance___10) %>%
  mutate(across(patient_insurance___1:patient_insurance___10, ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(
    by = site_type,
    label = list(
      "patient_insurance___1" ~ "State market place",
      "patient_insurance___2" ~ "Employer provided",
      "patient_insurance___3" ~ "Medicaid",
      "patient_insurance___4" ~ "Medicare - Original Medicare",
      "patient_insurance___5" ~ "Medicare - Advantage Plan",
      "patient_insurance___6" ~ "Worker's Comp",
      "patient_insurance___7" ~ "Other",
      "patient_insurance___8" ~ "Self-pay",
      "patient_insurance___9" ~ "Uninsured",
      "patient_insurance___10" ~ "Prefer not to answer",
      "patient_insurance___11" ~ "Medigap",
      "patient_insurance___12" ~ "Medicare Part D"
    ),
    value = everything() ~ "1"
  ) %>%
    add_overall() %>% add_p()
```

## Patient education level
```{r}
# Patient education level
t1 %>%
  select(patient_school, site_type) %>%
  tbl_summary(by = site_type,
    label = list(patient_school ~ "Patient education level")
  ) %>%
    add_overall() %>% add_p()
```

## Patient marital status
```{r}
t1 %>%
  select(patient_marital, site_type) %>%
  tbl_summary(by = site_type,
    label = list(patient_marital ~ "Patient marital status")
  ) %>%
    add_overall() %>% add_p()
```

## Patient employment status pre- long COVID
```{r}
t1 %>%
  select(site_type, patient_employ___1:patient_employ___7) %>%
  mutate(across(patient_employ___1:patient_employ___7, ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary( by = site_type,
    label = list(
      patient_employ___1 ~ "Employed Full-time",
      patient_employ___2 ~ "Employed Part-time",
      patient_employ___3 ~ "Unemployed",
      patient_employ___4 ~ "Disabled",
      patient_employ___5 ~ "Retired",
      patient_employ___6 ~ "Student",
      patient_employ___7 ~ "Other"
    ),
    value = everything() ~ "1"
  ) %>%
    add_overall() %>% add_p()
```

## Patient employment status current
```{r}
t1 %>%
  select(site_type, patient_employ_2___1:patient_employ_2___7) %>%
  mutate(across(patient_employ_2___1:patient_employ_2___7, ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(by = site_type,
    label = list(
      patient_employ_2___1 ~ "Employed Full-time",
      patient_employ_2___2 ~ "Employed Part-time",
      patient_employ_2___3 ~ "Unemployed",
      patient_employ_2___4 ~ "Disabled",
      patient_employ_2___5 ~ "Retired",
      patient_employ_2___6 ~ "Student",
      patient_employ_2___7 ~ "Other"
      ),
    value = everything() ~ "1"
  ) %>%
    add_overall() %>% add_p()
```

# Patient clinical questions
* Currently subsets to those that provided consent.

## 	For how many months do you feel you have had Long COVID symptoms (regardless of formal diagnosis)? (For example, 1 year would be 12 months; 2 years would be 24 months; 3 years would be 36 months) 
```{r}
t1 %>%
  select(months_symps, site_type) %>%
  tbl_summary(by = site_type,
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  ) %>%
  add_overall() %>% 
  add_p(
    everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE))
```


## Do you now have a diagnosis from a health care provider of Long COVID?
```{r}
t1 %>%
  select(lcdiagnosis, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### If yes, how many months did it take for you to get that diagnosis after your symptoms started? (For example, 1 year would be 12 months; 2 years would be 24 months; 3 years would be 36 months)
```{r}
t1 %>%
  filter(lcdiagnosis == "Yes") %>%
  select(
    site_type,
    ifyes_monthsymps) %>%
  tbl_summary(by = site_type,
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  ) %>%
  add_overall() %>% 
  add_p(
    everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE)
  )
```


## 	Which of the following conditions had you been diagnosed with prior to (before) developing Long COVID symptoms? (check all that apply)

```{r}
t1 %<>% 
  mutate(across(conditions___1:conditions___14, ~ factor(ifelse(.x == "Checked", 1, 0), levels = c(0, 1))))

# Order the condition from most frequent to least frequent
ordered_conditions <- t1 %>% 
  select(conditions___1:conditions___14) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(cols = everything(), names_to = "condition", values_to = "count") %>%
  arrange(desc(count)) %>%
  pull(condition)
```

```{r}
t1 %>%
  # select(conditions___1:conditions___14) %>%
  select(site_type, all_of(ordered_conditions)) %>%
  tbl_summary(by = site_type,
    label = list(
      "conditions___1" ~ "Hypertension",
      "conditions___2" ~ "Obesity",
      "conditions___3" ~ "Chronic lung disease (COPD, asthma, pulmonary fibrosis)",
      "conditions___4" ~ "Diabetes Mellitus",
      "conditions___5" ~ "Chronic immune suppression (organ transplant, HIV)",
      "conditions___6" ~ "Coronary artery disease",
      "conditions___7" ~ "High cholesterol",
      "conditions___8" ~ "Heart arrhythmias",
      "conditions___9" ~ "Major depression",
      "conditions___10" ~ "Anxiety",
      "conditions___11" ~ "PTSD",
      "conditions___12" ~ "Cancer",
      "conditions___13" ~ "Other (please describe)",
      "conditions___14" ~ "None"),
    value = everything() ~ "1"
  ) %>%
  add_overall() %>% 
  add_p()
```


```{r}
# All who selected "Other" did not provide free text so far
# commented here 
other_condition_n <- t1 %>%
  filter(conditions___14 == 1) %>%
  select(conditions_other) %>%
  drop_na() %>%
  nrow()

if (other_condition_n >= 1) {
  t1 %>%
    filter(conditions___14 == 1) %>%
    select(conditions_other) %>%
    tbl_summary()
}
```

## Have you received or increased your dose of any of the following medications specifically for Long COVID or Long COVID symptoms? (select all that apply)
```{r}
# Order the medications from most frequent to least frequent
t1 %<>% 
  mutate(across(medications___1:medications___13, ~ factor(ifelse(.x == "Checked", 1, 0), levels = c(0, 1))))

ordered_medications <- t1 %>% 
  select(medications___1:medications___13) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(cols = everything(), names_to = "medication", values_to = "count") %>%
  arrange(desc(count)) %>%
  pull(medication)
``` 

```{r}
t1 %>%
  # select(medications___1:medications___13) %>%
  select(site_type, all_of(ordered_medications)) %>%  
  tbl_summary(by = site_type,
    label = list(
      "medications___1" ~ "Paxlovid",
      "medications___2" ~ "Low dose naltrexone",
      "medications___3" ~ "Heart rate controlling agents (beta-blockers, calcium channel blockers, ivabradine)",
      "medications___4" ~ "Prednisone",
      "medications___5" ~ "Lung inhaler medications (Symbicort, Advair/Wixela, Breo)",
      "medications___6" ~ "Midodrine",
      "medications___7" ~ "Fludricortisone",
      "medications___8" ~ "SSRIs/SNRIs",
      "medications___9" ~ "Memantine",
      "medications___10" ~ "Adderall/Ritalin",
      "medications___11" ~ "Modafinil",
      "medications___12" ~ "Other (please specify)",
      "medications___13" ~ "None"),
    value = everything() ~ "1"
  ) %>%
    add_overall() %>% add_p()
```

### Other medicine (please specify)
```{r}
# All who selected "Other" 
other_medication_n <- t1 %>%
  filter(medications___13 == 1) %>%
  select(other_med) %>%
  drop_na() %>%
  nrow()

if (other_medication_n >= 1) {
  t1 %>%
    filter(medications___13 == 1) %>%
    select(other_med) %>%
    tbl_summary()
}
```

## Have you received any of the following therapies specifically for Long COVID or Long COVID symptoms? (select all that apply)
```{r}
t1 %<>%
  mutate(across(therapies___13:therapies___21, ~ factor(ifelse(.x == "Checked", 1, 0), levels = c(0, 1))))

ordered_therapies <- t1 %>%
  select(therapies___13:therapies___21) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(cols = everything(), names_to = "therapy", values_to = "count") %>%
  arrange(desc(count)) %>%
  pull(therapy)
``` 

```{r}
t1 %>%
  # select(therapies___13:therapies___21) %>%
  select(site_type, all_of(ordered_therapies)) %>%
  tbl_summary(by = site_type,
    label = list(
      "therapies___13" ~ "Speech therapy/cognitive training",
      "therapies___14" ~ "Physical therapy",
      "therapies___15" ~ "Occupational therapy",
      "therapies___16" ~ "Group therapy/peer support",
      "therapies___17" ~ "Pulmonary rehab",
      "therapies___18" ~ "Counseling/mental or behavioral health therapy",
      "therapies___19" ~ "Complementary/alternative therapies (examples like acupuncture, supplements, chiropractic, etc.)",
      "therapies___20" ~ "Other (please specify)",
      "therapies___21" ~ "None"),
    value = everything() ~ "1"
  ) %>%
  add_overall() %>% 
  add_p()
```

## Other services (please specify)
```{r}
# All who selected "Other" 
other_therapies_n <- t1 %>%
  filter(therapies___20 == 1) %>%
  select(other_med) %>%
  drop_na() %>%
  nrow()

if (other_therapies_n >= 1) {
  t1 %>%
    filter(therapies___20 == 1) %>%
    select(other_service) %>%
    tbl_summary()
}
```

# PROMIS Global Health
## Global physical and mental health subscores
* PROMIS physical health and mental health subscores range from 4 (min) - 20 (max) 
```{r}
# Prep the promis variables. For t1, the names of the columns do not match with
# the columns in the scoring guide. The following code chunk is designed to 
# harmonize the names of the RedCap variables with those in the scoring guide. 
# In addition, labeled variables are converted to numerical for the calculation
# of the raw scores, and other variables are cleaned up
t1 %<>%
  # select(promis_global01:avg_pain) %>%
  rename(
    promis_global09r = promis_global06,
    promis_global06 = promis_global07,
    promis_global10r = bothered,
    promis_global08r = avg_fatigue,
    promis_global07r = avg_pain) %>%
  mutate(across(promis_global02:promis_global05, ~ as.numeric(substr(.x, 1, 1)))) %>%
  mutate(promis_global06 = as.numeric(substr(promis_global06, 1, 1))) %>%
  mutate(promis_global07r = case_match(
    promis_global07r,
    "0 No pain" ~ 5,
    c("1", "2", "3") ~ 4,
    c("4", "5", "6") ~ 3,
    c("7", "8", "9") ~ 2,
    "10 Worst pain imagin-able" ~ 1,    
    .default = NA)) %>%
  mutate(promis_global08r = case_match(
    promis_global08r,
      "None" ~ 5,
      "Mild" ~ 4,
      "Moderate" ~ 3, 
      "Severe" ~ 2,
      "Very severe" ~ 1,
      .default = NA)) %>%
  mutate(promis_global10r = case_match(
    promis_global10r,
      "Never" ~ 5,
      "Rarely" ~ 4,
      "Sometimes" ~ 3, 
      "Often" ~ 2,
      "Always" ~ 1,
      .default = NA)) %>%
  mutate(across(c(promis_global01, promis_global09r), ~ 
  factor(str_trim(sub("^[^-]*-", "", .x)), levels = c("Excellent", "Very good", "Good", "Fair", "Poor")))) %>%
  mutate(promis_global_phys = rowSums(across(c(promis_global07r, promis_global06, promis_global03, promis_global08r)))) %>%
  mutate(promis_global_ment = rowSums(across(c(promis_global02, promis_global04, promis_global05, promis_global10r))))
```

```{r}
t1 %>%
  select(site_type, promis_global_phys, promis_global_ment) %>%
  tbl_summary(site_type,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      promis_global_phys ~ "Global physical health",
      promis_global_ment ~ "Global mental health"
    )
  ) %>%
  add_overall() %>%
  add_p(everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE))
```


<!-- ////////////////////////// PROMIS T2 for Jun //////////////////////////-->
<!-- The following two code chunks are for outputting for Jun 01/08/2025 -->
```{r}
#| eval: false

# In T2 and beyond the column names of the PROMIS change
# promis_global01_v2
# promis_global02_v2
# promis_global03_v2
# promis_global03_v2
# promis_global04_v2
# promis_global05_v2
# promis_global06_v2
# promis_global07_v2
# bothered_v2
# avg_fatigue_v2
# avg_pain_v2
t2 %<>%
  select(-(promis_global01:avg_pain)) %>% # Remove the columns from the T1 event to rename properly
  rename(
    promis_global01 = promis_global01_v2,
    promis_global02 = promis_global02_v2,
    promis_global03 = promis_global03_v2,
    promis_global04 = promis_global04_v2,
    promis_global05 = promis_global05_v2,
    promis_global06 = promis_global07_v2,
    promis_global07r = avg_pain_v2,
    promis_global08r = avg_fatigue_v2,
    promis_global09r = promis_global06_v2,
    promis_global10r = bothered_v2) %>%
  mutate(across(promis_global02:promis_global05, ~ as.numeric(substr(.x, 1, 1)))) %>%
  mutate(promis_global06 = as.numeric(substr(promis_global06, 1, 1))) %>%
  mutate(promis_global07r = case_match(
    promis_global07r,
    "0 No pain" ~ 5,
    c("1", "2", "3") ~ 4,
    c("4", "5", "6") ~ 3,
    c("7", "8", "9") ~ 2,
    "10 Worst pain imagin-able" ~ 1,    
    .default = NA)) %>%
  mutate(promis_global08r = case_match(
    promis_global08r,
      "None" ~ 5,
      "Mild" ~ 4,
      "Moderate" ~ 3, 
      "Severe" ~ 2,
      "Very severe" ~ 1,
      .default = NA)) %>%
  mutate(promis_global10r = case_match(
    promis_global10r,
      "Never" ~ 5,
      "Rarely" ~ 4,
      "Sometimes" ~ 3, 
      "Often" ~ 2,
      "Always" ~ 1,
      .default = NA)) %>%
  mutate(across(c(promis_global01, promis_global09r), ~ 
  factor(str_trim(sub("^[^-]*-", "", .x)), levels = c("Excellent", "Very good", "Good", "Fair", "Poor")))) %>%
  mutate(promis_global_phys = rowSums(across(c(promis_global07r, promis_global06, promis_global03, promis_global08r)))) %>%
  mutate(promis_global_ment = rowSums(across(c(promis_global02, promis_global04, promis_global05, promis_global10r))))
```

```{r}
#| eval: false
t2 %>%
  select(promis_global_phys, promis_global_ment) %>%
  tbl_summary(,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      promis_global_phys ~ "Global physical health",
      promis_global_ment ~ "Global mental health"
    )
  ) %>%
  as_gt() %>%
  gt::gtsave("t2_promis_raw_scores.docx", path = "D:\\long_covid\\patient_survey")
```
<!-- ////////////////////////////////////////////////////////////////////// -->


## Promis Global Health Physical and Mental Health T-Scores

```{r}
# Calculate the PROMIS T-scores

# load the t-score tables
promis_global_pht <- read_csv("D:\\long_covid\\patient_survey\\scoring_guides\\promis_phys_t-score_table.csv",
  show_col_types = FALSE)

promis_global_mht <- read_csv("D:\\long_covid\\patient_survey\\scoring_guides\\promis_ment_t-score_table.csv",
  show_col_types = FALSE)
```

```{r}
# Merge in global physical health scores
t1 %<>%
  left_join(
    promis_global_pht %>% select(-SE),
    by = c("promis_global_phys" = "Raw Summed Score")
  ) %>%
  rename(promis_pht = "T-Score")

# Merg in the mental health scores
t1 %<>%
  left_join(
    promis_global_mht %>% select(-SE),
    by = c("promis_global_ment" = "Raw Summed Score")
  ) %>%
  rename(promis_mht = "T-Score")
```

```{r}
# Display the tables of T-Score and their averages
t1 %>%
  select(site_type, promis_pht, promis_mht) %>%
  tbl_summary(by = site_type,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      promis_pht ~ "Global physical health T-score",
      promis_mht ~ "Global mental health T-score"
      # promis_global01 ~ "In general, would you say your health is:",
      # promis_global09r ~ "In general, please rate how well you carry out your usual social activities and roles."
    )
  ) %>%
  add_overall() %>% 
  add_p(
    everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE)
  )
```

## In general, would you say your health is:
```{r}
t1 %>%
  select(site_type, promis_global01) %>%
  tbl_summary(by = site_type,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      # promis_global_phys ~ "Global physical health",
      # promis_global_ment ~ "Global mental health",
      # promis_global01 ~ "In general, would you say your health is:",
      # promis_global09r ~ "In general, please rate how well you carry out your usual social activities and roles."
    )
  ) %>%
    add_overall() %>% add_p()
```


## In general, please rate how well you carry out your usual social activities and roles.
```{r}
t1 %>%
  select(promis_global09r, site_type) %>%
  tbl_summary(by = site_type,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      # promis_global_phys ~ "Global physical health",
      # promis_global_ment ~ "Global mental health",
      # promis_global01 ~ "In general, would you say your health is:",
      # promis_global09r ~ "In general, please rate how well you carry out your usual social activities and roles."
    )
  ) %>%
    add_overall() %>% add_p()
```

<!-- ////////////////////////////////////////////////////////////////////// -->
```{r}
#| eval: false
# Merge in global physical health scores
t2 %<>%
  left_join(
    promis_global_pht %>% select(-SE),
    by = c("promis_global_phys" = "Raw Summed Score")
  ) %>%
  rename(promis_pht = "T-Score")

# Merge in the mental health scores
t2 %<>%
  left_join(
    promis_global_mht %>% select(-SE),
    by = c("promis_global_ment" = "Raw Summed Score")
  ) %>%
  rename(promis_mht = "T-Score")
```

```{r}
#| eval: false
# Display the tables of T-Score and their averages
t2 %>%
  select(promis_pht, promis_mht) %>%
  tbl_summary(,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      promis_pht ~ "Global physical health T-score",
      promis_mht ~ "Global mental health T-score"
      # promis_global01 ~ "In general, would you say your health is:",
      # promis_global09r ~ "In general, please rate how well you carry out your usual social activities and roles."
    )
  ) %>%
  as_gt() %>%
  gt::gtsave("t2_promis_t_scores.docx", path = "D:\\long_covid\\patient_survey")
```

<!-- ////////////////////////////////////////////////////////////////////// -->

# PASC
## Do you think you currently have symptoms or health problems resulting from your COVID infection?
```{r}
t1 %>%
  select(ps_ptpasc, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

<!-- ////////////////////////////////////////////////////////////////////// -->
```{r}
#| eval: false
t2 %>%
  select(ps2_ptpasc) %>%
  tbl_summary() %>%
  as_gt() %>%
  gt::gtsave("t2_ptpasc.docx","D:\\long_covid\\patient_survey" )
```
<!-- ////////////////////////////////////////////////////////////////////// -->
## Symptoms
* n.b. denominator is a subset to those that answered "Yes" to the question "Do you think you currently have symptoms or health problems resulting from your COVID infection?"
* n.b. denominator for ps_menstrual and ps_menopause is a subset to the above and a response of "Female", "Transgender Male", "Non-binary", "Other, please describe", or "Prefer not to answer" to the question What is your gender identity?

### Overall
```{r}
# This chunk begins the section for generating the multi-colored figure in the
# report.
core_symptoms <- t1 %>%
  select(ps_fatigue:ps_sex) %>%
  names()

# Another option is to display as a chart with binary responses
pasc_hist <- t1 %>%
  filter(ps_ptpasc == "Yes") %>%
  select(all_of(core_symptoms)) %>%
  mutate(across(everything(), ~ ifelse(str_detect(.x, "Yes"), 1, 0))) %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "yes") %>%
  group_by(symptom) %>%
  summarise(total_endorsed = sum(yes)) %>%
  mutate(symptom = factor(symptom, levels = core_symptoms))
 
# Get a denominator all patients
denominator_all <- t1 %>%
  filter(ps_ptpasc == "Yes") %>%
  nrow()

# Get a denominator for ps_menstrual:ps_menopause which is a subset of those
# that are not Male or Transgender Female
denominator_subset <- t1 %>%
  filter(ps_ptpasc == "Yes") %>%
  filter(!patient_gender %in% c("Male", "Transgender Female")) %>%
  select(patient_gender, ps_menstrual:ps_menopause) %>%
  nrow()

pasc_hist %<>%
  mutate(percent = str_c("(",
    round(
      ifelse(symptom %in% c("ps_menstrual", "ps_menopause"), total_endorsed / denominator_subset, total_endorsed / denominator_all),
      2) * 100, "%)")) %>%
  mutate(n_per = str_c(total_endorsed, " ", percent))

ordered_symptoms <- pasc_hist %>%
  arrange(total_endorsed) %>%
  pull(symptom)
```

```{r, fig.height = 6.5, fig.width=6.5, fig.dpi = 600}
pasc_hist %>%
  mutate(symptom = factor(symptom, levels = ordered_symptoms)) %>%
  ggplot(aes(x = symptom, y = total_endorsed, fill = symptom)) +
  geom_col() +
  geom_text(
    aes(label = n_per), 
          hjust = -0.25,
          size = 3) +  
  theme_minimal() +
  lims(y = c(0, 35)) +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x = "Symptom", y = "Number endorsed (percent)")
```


### MDC
```{r}
core_symptoms <- t1 %>%
  select(ps_fatigue:ps_sex) %>%
  names()

# Another option is to display as a chart with binary responses
pasc_hist <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "MDC") %>%
  select(all_of(core_symptoms)) %>%
  mutate(across(everything(), ~ ifelse(str_detect(.x, "Yes"), 1, 0))) %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "yes") %>%
  group_by(symptom) %>%
  summarise(total_endorsed = sum(yes)) %>%
  mutate(symptom = factor(symptom, levels = core_symptoms))
 
# Get a denominator all patients
denominator_all <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "MDC") %>%
  nrow()

# Get a denominator for ps_menstrual:ps_menopause which is a subset of those
# that are not Male or Transgender Female
denominator_subset <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "MDC") %>%
  filter(!patient_gender %in% c("Male", "Transgender Female")) %>%
  select(patient_gender, ps_menstrual:ps_menopause) %>%
  nrow()

pasc_hist %<>%
  mutate(percent = str_c("(",
    round(
      ifelse(symptom %in% c("ps_menstrual", "ps_menopause"), total_endorsed / denominator_subset, total_endorsed / denominator_all),
      2) * 100, "%)")) %>%
  mutate(n_per = str_c(total_endorsed, " ", percent))

ordered_symptoms <- pasc_hist %>%
  arrange(total_endorsed) %>%
  pull(symptom)
```

```{r, fig.height = 6.5, fig.width=6.5, fig.dpi = 600}
pasc_hist %>%
  mutate(symptom = factor(symptom, levels = ordered_symptoms)) %>%
  ggplot(aes(x = symptom, y = total_endorsed, fill = symptom)) +
  geom_col() +
  geom_text(
    aes(label = n_per), 
          hjust = -0.25,
          size = 3) +  
  theme_minimal() +
  lims(y = c(0, 35)) +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x = "Symptom", y = "Number endorsed (percent)")
```

### PCC
```{r}
core_symptoms <- t1 %>%
  select(ps_fatigue:ps_sex) %>%
  names()

# Another option is to display as a chart with binary responses
pasc_hist <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "PCC") %>%
  select(all_of(core_symptoms)) %>%
  mutate(across(everything(), ~ ifelse(str_detect(.x, "Yes"), 1, 0))) %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "yes") %>%
  group_by(symptom) %>%
  summarise(total_endorsed = sum(yes)) %>%
  mutate(symptom = factor(symptom, levels = core_symptoms))
 
# Get a denominator all patients
denominator_all <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "PCC") %>%
  nrow()

# Get a denominator for ps_menstrual:ps_menopause which is a subset of those
# that are not Male or Transgender Female
denominator_subset <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "PCC") %>%
  filter(!patient_gender %in% c("Male", "Transgender Female")) %>%
  select(patient_gender, ps_menstrual:ps_menopause) %>%
  nrow()

pasc_hist %<>%
  mutate(percent = str_c("(",
    round(
      ifelse(symptom %in% c("ps_menstrual", "ps_menopause"), total_endorsed / denominator_subset, total_endorsed / denominator_all),
      2) * 100, "%)")) %>%
  mutate(n_per = str_c(total_endorsed, " ", percent))

ordered_symptoms <- pasc_hist %>%
  arrange(total_endorsed) %>%
  pull(symptom)
```

```{r, fig.height = 6.5, fig.width=6.5, fig.dpi = 600}
pasc_hist %>%
  mutate(symptom = factor(symptom, levels = ordered_symptoms)) %>%
  ggplot(aes(x = symptom, y = total_endorsed, fill = symptom)) +
  geom_col() +
  geom_text(
    aes(label = n_per), 
          hjust = -0.25,
          size = 3) +  
  theme_minimal() +
  lims(y = c(0, 35)) +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x = "Symptom", y = "Number endorsed (percent)")
```

```{r}
# These are the 12 symptoms used to calculate a PASC score
pasc_symptoms <- c(
"ps_sense",
"ps_malaise",
"ps_cough",
"ps_think",
"ps_thirst",
"ps_heart",
"ps_pain",
"ps_fatigue",
"ps_sex",
"ps_faint",
"ps_gastro",
"ps_nerve")

# These are the weights to multiply each binary symptom value
pasc_symptom_scores <- c(8, 7, 4, 3, 3, 2, 2, 1, 1, 1, 1, 1)
```

## PASC Scores
```{r}
# Multiply each symptom column with the corresponding symptom weight then merge 
# the data back into the main t1 data frame when filtered, only to those that
# had the pasc administered. Merging into the filtered t1 data frame was 
# performed in case study team wants to see the scores broken out by clinic
# gender, age, or some other variable.
t1 %>%
  filter(ps_ptpasc == "Yes") %>%
  bind_cols(
    ., 
    (t1 %>%
      filter(ps_ptpasc == "Yes") %>%
      select(all_of(pasc_symptoms)) %>%
      mutate(across(everything(), ~ ifelse(str_detect(.x, "Yes"), 1, 0))) %>%
      sweep(., 2, pasc_symptom_scores, `*`) %>%
      mutate(pasc_score = rowSums(across(everything()))) %>%
      mutate(pasc_positive = ifelse(pasc_score >= 12, 1, 0)) %>%
      select(pasc_score, pasc_positive))
  ) %>%
  select(site_type, pasc_score, pasc_positive) %>%
  tbl_summary(by = site_type,
    statistic = list(pasc_score ~ "{mean} ({sd}); [{min}, {median}, {max}]"),
    value = list(pasc_positive ~ "1")
  ) %>%
  add_overall() %>% 
  add_p(
    everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE)
  )
```


<!-- ////////////////////////////////////////////////////////////////////// -->
```{r}
#| eval: false
# Rename the t2 columns, to recycle/repurpose the t1 code
t2_pasc <- 
  t2 %>% 
  select(starts_with("ps2"))

t2_pasc_names <- names(t2_pasc)

new_t2_pasc_names <- str_replace(t2_pasc_names, "ps2_", "ps_")

names(t2_pasc) <- new_t2_pasc_names

t2 %<>%
  select(-(starts_with("ps2"))) %>%
  select(-(starts_with("ps")))

t2 %<>%
  bind_cols(t2_pasc)
```

```{r}
#| eval: false
t2 %>%
  filter(ps_ptpasc == "Yes") %>%
  bind_cols(
    ., 
    (t2 %>%
      filter(ps_ptpasc == "Yes") %>%
      select(all_of(pasc_symptoms)) %>%
      mutate(across(everything(), ~ ifelse(str_detect(.x, "Yes"), 1, 0))) %>%
      sweep(., 2, pasc_symptom_scores, `*`) %>%
      mutate(pasc_score = rowSums(across(everything()))) %>%
      mutate(pasc_positive = ifelse(pasc_score >= 12, 1, 0)) %>%
      select(pasc_score, pasc_positive))
  ) %>%
  select(pasc_score, pasc_positive) %>%
  tbl_summary(
    statistic = list(pasc_score ~ "{mean} ({sd}); [{min}, {median}, {max}]"),
    value = list(pasc_positive ~ "1")
  ) %>%
  as_gt() %>%
  gt::gtsave("t2_pasc_scores.docx", "D:\\long_covid\\patient_survey")
```

<!-- ////////////////////////////////////////////////////////////////////// -->


## Average symptom burden, severity, and frequency
* Symptoms ordered by frequency as in the previous chart
* All burden, severity, and frequency questions are branched and presented only if patient responded endorsed experiencing the given symptom.
* "ps_sense", "ps_headache", "ps_itching", "ps_bald", "ps_menstrual", "ps_menopause", "ps_fertility" "ps_sex" not assessed for frequency or severity.

```{r}
# Display a table of the burden, severity, and frequency 
# To display a table where each column represents the mean of burden, frequency, and severity
# might be good to get a long data frame with 3 variables, symptom, value, dimension

# Import data as numerical since there are inconsistencies in the values/response options for each
# symptom, so designing an algorithm like mutate(across(cols)) to convert the label values to numeric
# would not be wise

pasc_severity_data <- 
  pull_redcap_report(Sys.getenv("LC_patient"), "176060", "raw", "raw", "false") %>%
  select(
    promis_record_id, 
    redcap_event_name,
    starts_with("ps_")) %>%
  filter(
    redcap_event_name == "consent_and_t1_sur_arm_1", 
    promis_record_id %in% t1$record_id)
```

```{r}
pasc_severity_data <- pasc_severity_data %>%
  rename(
    ps_headache_freqdepaul = ps_headache_freq,
    ps_headache_sevdepaul = ps_headache_sev,
    ps_itching_burden = ps_itching_itchburden,
    ps_itching_freqdepaul = ps_itching_itchfreq,
    ps_itching_sevdepaul = ps_itching_itchsev,
    record_id = promis_record_id) %>%
  mutate(across(starts_with("ps_"), ~ifelse(.x == -88, NA, .x))) %>%
  # mutate(across(ends_with("sevdepaul") | ends_with("freqdepaul"), ~ ifelse(.x == -88, NA, .x))) %>%
  mutate(across(ends_with("sevdepaul") | ends_with("freqdepaul"), ~ .x + 1))
# ------------------------------------------------------
```

```{r}
# Create a df of the burden dimension columns
burden_df <- pasc_severity_data %>%
  select(ends_with("burden"))

# Get the names of the burden columns, to rename them so that there is common naming scheming
# to display burden, frequency and severity.
burden_names <- names(burden_df)

# Remove everything after the 1st underscore from the right 
burden_names_modified <- sub("_[^_]*$", "", burden_names)

# Set the new names
names(burden_df) <- burden_names_modified

# Convert to long format
burden_df_long <- burden_df %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "response") %>%
  mutate(dimension = "burden")

# ------------------------------------------------------
severity_df <- pasc_severity_data %>%
  select(ends_with("sevdepaul"))

# Get the names
severity_names <- names(severity_df)

# Remove everything after the 1st underscore from the right
severity_names_modified <- sub("_[^_]*$", "", severity_names)

# Set the new names
names(severity_df) <- severity_names_modified

# Convert to long format
severity_df_long <- severity_df %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "response") %>%
  mutate(dimension = "severity")

# ------------------------------------------------------
frequency_df <- pasc_severity_data %>%
  select(ends_with("freqdepaul"))

frequency_names <- names(frequency_df)

frequency_names_modified <-  sub("_[^_]*$", "", frequency_names)

names(frequency_df) <- frequency_names_modified

frequency_df_long <- frequency_df %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "response") %>%
  mutate(dimension = "frequency")

# The following symptoms did not have data for severity nor frequency
# "ps_sense" "ps_sex" "ps_menstrual" "ps_menopause" "ps_fertility" 
# "ps_bald" dos not have frequency 
```

```{r}
df_long <- bind_rows(
  burden_df_long,
  frequency_df_long,
  severity_df_long
) %>%
mutate(response = ifelse(response == -88, NA, response)) %>%
group_by(symptom, dimension) %>%
summarise(mean = mean(response, na.rm = TRUE), .groups = "drop")
```

### Overall
```{r, fig.height = 8, fig.width=6.5, fig.dpi = 600}
df_long %>%
  mutate(symptom = factor(symptom, levels = fct_recode(ordered_symptoms, "ps_eyedry" = "ps_dryeyes") )) %>%
  ggplot(., aes(x = dimension, y = symptom, fill = mean)) +
  geom_tile(color = "white", linewidth = 0.5, width = 0.5) +
  geom_text(aes(label = scales::number(mean, accuracy = 0.01)), color = "white", size = 3.5) +
  scale_fill_gradient(
    low = "steelblue",
    high = "tomato",
    guide = "none") +
  labs(
    title = "", 
    x = "Dimension", 
    y = "Symptom") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    # axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right") +
  scale_y_discrete(expand = c(0, 0)) +            # remove y padding
  coord_fixed(ratio = .3) +                       # taller cells → slimmer columnslook
  theme_minimal(base_size = 12)                   # add grid lines
```


### MDC
```{r}
# Create a df of the burden dimension columns
burden_df <- 
  left_join(
    t1 %>% select(record_id, site_type),
    pasc_severity_data,
    by = "record_id") %>%
  filter(site_type == "MDC") %>%
  select(ends_with("burden"))

# Get the names of the burden columns, to rename them so that there is common naming scheming
# to display burden, frequency and severity.
burden_names <- names(burden_df)

# Remove everything after the 1st underscore from the right 
burden_names_modified <- sub("_[^_]*$", "", burden_names)

# Set the new names
names(burden_df) <- burden_names_modified

# Convert to long format
burden_df_long <- burden_df %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "response") %>%
  mutate(dimension = "burden")

# ------------------------------------------------------
severity_df <- pasc_severity_data %>%
  select(ends_with("sevdepaul"))

# Get the names
severity_names <- names(severity_df)

# Remove everything after the 1st underscore from the right
severity_names_modified <- sub("_[^_]*$", "", severity_names)

# Set the new names
names(severity_df) <- severity_names_modified

# Convert to long format
severity_df_long <- severity_df %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "response") %>%
  mutate(dimension = "severity")

# ------------------------------------------------------
frequency_df <- pasc_severity_data %>%
  select(ends_with("freqdepaul"))

frequency_names <- names(frequency_df)

frequency_names_modified <-  sub("_[^_]*$", "", frequency_names)

names(frequency_df) <- frequency_names_modified

frequency_df_long <- frequency_df %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "response") %>%
  mutate(dimension = "frequency")
```

```{r}
df_long <- bind_rows(
  burden_df_long,
  frequency_df_long,
  severity_df_long
) %>%
mutate(response = ifelse(response == -88, NA, response)) %>%
group_by(symptom, dimension) %>%
summarise(mean = mean(response, na.rm = TRUE), .groups = "drop")
```


```{r, fig.height = 8, fig.width=6.5, fig.dpi = 600}
df_long %>%
  mutate(symptom = factor(symptom, levels = fct_recode(ordered_symptoms, "ps_eyedry" = "ps_dryeyes") )) %>%
  ggplot(., aes(x = dimension, y = symptom, fill = mean)) +
  geom_tile(color = "white", linewidth = 0.5, width = 0.5) +
  geom_text(aes(label = scales::number(mean, accuracy = 0.01)), color = "white", size = 3.5) +
  scale_fill_gradient(
    low = "steelblue",
    high = "tomato",
    guide = "none") +
  labs(
    title = "", 
    x = "Dimension", 
    y = "Symptom") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    # axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right") +
  scale_y_discrete(expand = c(0, 0)) +            # remove y padding
  coord_fixed(ratio = .3) +                       # taller cells → slimmer columnslook
  theme_minimal(base_size = 12)                   # add grid lines
```

### PCC
```{r}
# Create a df of the burden dimension columns
burden_df <- 
  left_join(
    t1 %>% select(record_id, site_type),
    pasc_severity_data,
    by = "record_id") %>%
  filter(site_type == "PCC") %>%
  select(ends_with("burden"))

# Get the names of the burden columns, to rename them so that there is common naming scheming
# to display burden, frequency and severity.
burden_names <- names(burden_df)

# Remove everything after the 1st underscore from the right 
burden_names_modified <- sub("_[^_]*$", "", burden_names)

# Set the new names
names(burden_df) <- burden_names_modified

# Convert to long format
burden_df_long <- burden_df %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "response") %>%
  mutate(dimension = "burden")

# ------------------------------------------------------
severity_df <- pasc_severity_data %>%
  select(ends_with("sevdepaul"))

# Get the names
severity_names <- names(severity_df)

# Remove everything after the 1st underscore from the right
severity_names_modified <- sub("_[^_]*$", "", severity_names)

# Set the new names
names(severity_df) <- severity_names_modified

# Convert to long format
severity_df_long <- severity_df %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "response") %>%
  mutate(dimension = "severity")

# ------------------------------------------------------
frequency_df <- pasc_severity_data %>%
  select(ends_with("freqdepaul"))

frequency_names <- names(frequency_df)

frequency_names_modified <-  sub("_[^_]*$", "", frequency_names)

names(frequency_df) <- frequency_names_modified

frequency_df_long <- frequency_df %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "response") %>%
  mutate(dimension = "frequency")
```

```{r}
df_long <- bind_rows(
  burden_df_long,
  frequency_df_long,
  severity_df_long
) %>%
mutate(response = ifelse(response == -88, NA, response)) %>%
group_by(symptom, dimension) %>%
summarise(mean = mean(response, na.rm = TRUE), .groups = "drop")
```


```{r, fig.height = 8, fig.width=6.5, fig.dpi = 600}
df_long %>%
  drop_na() %>%
  mutate(symptom = factor(symptom, levels = fct_recode(ordered_symptoms, "ps_eyedry" = "ps_dryeyes") )) %>%
  ggplot(., aes(x = dimension, y = symptom, fill = mean)) +
  geom_tile(color = "white", linewidth = 0.5, width = 0.5) +
  geom_text(aes(label = scales::number(mean, accuracy = 0.01)), color = "white", size = 3.5) +
  scale_fill_gradient(
    low = "steelblue",
    high = "tomato",
    guide = "none") +
  labs(
    title = "", 
    x = "Dimension", 
    y = "Symptom") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    # axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right") +
  scale_y_discrete(expand = c(0, 0)) +            # remove y padding
  coord_fixed(ratio = .3) +                       # taller cells → slimmer columnslook
  theme_minimal(base_size = 12)                   # add grid lines
```



# Experiences of Stigma
## Have you had one or more appointments with medical providers at a primary care clinic in the past three months?
```{r}
t1 %>%
  select(pcc_appts, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```


## Mean score of "lack of understanding" scale from Illness Invalidation Inventory for PCC
* n.b. Subsets to those that answered "Yes" to the question "Have you had one or more appointments with medical providers at a primary care clinic in the past three months?" or "Have you had one or more appointments with medical providers at a multi-disciplinary Long COVID clinic in the past three months?"
* Scale ranges from 1(min) to 5(max), with 1 indicating the lowest perceived understanding from medical providers and 5 indicated the highest perceived understanding.

```{r}
t1 %>%
  filter(pcc_appts == "Yes") %>%
  select(site_type, serious_pcc:talk_pcc) %>%
  mutate(across(serious_pcc:talk_pcc, ~ case_match(.x, 
      "Never" ~ 1,
      "Rarely" ~ 2,
      "Sometimes" ~ 3, 
      "Often" ~ 4,
      "Very Often" ~ 5,
      .default = NA))) %>%
  mutate(na_counts = rowSums(is.na(across(serious_pcc:talk_pcc)))) %>%   
  mutate(score = rowMeans(across(serious_pcc:talk_pcc), na.rm = TRUE)) %>%
  mutate(score = ifelse(na_counts >= 2, NA, score)) %>%
  select(score, site_type) %>%
  tbl_summary(
    by = site_type,
    type = everything() ~ "continuous",
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]")  %>%
  add_overall() %>%
  add_p(
    everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE)
  )
```


<!-- INDIVIDUAL SCORES -->
## Individual questions: How often in the past 3 months did medical professionals at your primary care clinic react to you in the following ways:
### Medical professionals took me seriously.
```{r}
t1 %>%
  filter(pcc_appts == "Yes") %>%
  select(serious_pcc, site_type) %>%
  mutate(across(serious_pcc, ~ factor(.x, levels = c( 
      "Never",
      "Rarely",
      "Sometimes", 
      "Often",
      "Very Often")))) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Medical professionals understood the consequences of my health problems or illness.
```{r}
t1 %>%
  filter(pcc_appts == "Yes") %>%
  select(consequences_pcc, site_type) %>%
  mutate(across(consequences_pcc, ~ factor(.x, levels = c( 
      "Never",
      "Rarely",
      "Sometimes", 
      "Often",
      "Very Often")))) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Medical professionals gave me the chance to talk about what is on my mind.
```{r}
t1 %>%
  filter(pcc_appts == "Yes") %>%
  select(talk_pcc, site_type) %>%
  mutate(across(talk_pcc, ~ factor(.x, levels = c( 
      "Never",
      "Rarely",
      "Sometimes", 
      "Often",
      "Very Often")))) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

## Have you had one or more appointments with medical providers at a multi-disciplinary Long COVID clinic in the past three months?
```{r}
t1 %>%
  select(mdc_appts, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

<!-- INDIVIDUAL SCORES -->
## Individual questions: How often in the past 3 months did medical professionals at your multi-disciplinary Long COVID clinic react to you in the following ways:
```{r}
t1 %>%
  filter(mdc_appts == "Yes") %>%
  select(serious_mdc, site_type) %>%
  mutate(across(serious_mdc, ~ factor(.x, levels = c( 
      "Never",
      "Rarely",
      "Sometimes", 
      "Often",
      "Very Often")))) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Medical professionals understood the consequences of my health problems or illness.
```{r}
t1 %>%
  filter(mdc_appts == "Yes") %>%
  select(consequences_mdc, site_type) %>%
  mutate(across(consequences_mdc, ~ factor(.x, levels = c( 
      "Never",
      "Rarely",
      "Sometimes", 
      "Often",
      "Very Often")))) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Medical professionals gave me the chance to talk about what is on my mind.
```{r}
t1 %>%
  filter(mdc_appts == "Yes") %>%
  select(talk_mdc, site_type) %>%
  mutate(across(talk_mdc, ~ factor(.x, levels = c( 
      "Never",
      "Rarely",
      "Sometimes", 
      "Often",
      "Very Often")))) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```


# Health Related Social Needs
## Living Situation
### What is your living situation today?
```{r}
t1 %>%
  select(living_sit, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Think about the place you live. Do you have problems with any of the following?
```{r}
t1 %>%
  select(living_probs___1:living_probs___8, site_type) %>%
  mutate(across(living_probs___1:living_probs___8, ~ factor(ifelse(.x == "Checked", 1, 0), levels = c(0, 1)))) %>%
  tbl_summary(
    by = site_type,
    value = everything() ~ "1",
    label = list(
      living_probs___1 ~ "Pests such as bugs, ants, or mice",
      living_probs___2 ~ "Mold",
      living_probs___3 ~ "Lead paint or pipes",
      living_probs___4 ~ "Lack of heat",
      living_probs___5 ~ "Oven or stove not working",
      living_probs___6 ~ "Smoke detectors missing or not working",
      living_probs___7 ~ "Water leaks",
      living_probs___8 ~ "None of the above"
    )
  ) %>%
  add_overall() %>% 
  add_p()
```

## Food
### Within the past 12 months, were you worried that your food would run out before you got money to buy more?
```{r}
t1 %<>%
  mutate(across(food_worry:food_last, ~ factor(.x, levels = c("Often true", "Sometimes true", "Never true"))))

t1 %<>%
  mutate(across(transport, ~ factor(.x, levels = c("Yes", "No"))))
```

```{r}
t1 %>%
  select(food_worry, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Within the past 12 months, has the food you bought just didn't last and you didn't have money to get more?
```{r}
t1 %>%
  select(food_last, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

## Transportation
### In the past 12 months, has lack of reliable transportation kept you from medical appointments, meetings, work or from getting things needed for daily living?
```{r}
t1 %>%
  select(transport, site_type) %>%
  tbl_summary( 
    by = site_type,
    type = list(transport ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

## Utilities
### In the past 12 months has the electric, gas, oil, or water company threatened to shut off services in your home?
```{r}
t1 %>%
  select(utlities, site_type) %>%
  tbl_summary(
    by = site_type,
    type = list(utlities ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

## Financial Strain
### How hard is it for you to pay for the very basics like food, housing, medical care, and heating? Would you say it is:
```{r}
t1 %>%
  select(fin_strain, site_type) %>%
  tbl_summary( 
    by = site_type,
    type = list(fin_strain ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

## Family & Community Support
### If for any reason you need help with day-to-day activities such as bathing, preparing meals, shopping, managing finances, etc., do you get the help you need?
```{r}
t1 %>%
  select(help_daytoday, site_type) %>%
  mutate(help_daytoday = factor(help_daytoday, levels = c("I don't need any help", "I get all the help I need", "I could use a little more help", "I need a lot more help"))) %>%
  tbl_summary( by = site_type,
    type = list(help_daytoday ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

### How often do you feel lonely or isolated from those around you?
```{r}
t1 %>%
  select(lonely, site_type) %>%
  mutate(lonely = factor(lonely, levels = c("Never", "Rarely", "Sometimes", "Often", "Always"))) %>%
  tbl_summary( by = site_type,
    type = list(lonely ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

## Summary of needs by domain
```{r}
# Pull HRSN data as numerical values, filter to those in the t1 / tab_data (all consented so far)
hrsn_data <- 
  pull_redcap_report(Sys.getenv("LC_patient"), "176060", "raw", "raw", "false") %>%
  select(
    promis_record_id, 
    redcap_event_name,
    living_sit:lonely,
    pcc_or_mdc) %>%
  rename(site_type = pcc_or_mdc) %>% 
  group_by(promis_record_id) %>%
  fill(site_type, .direction = "updown") %>%
  ungroup() %>%
  mutate(site_type = ifelse(site_type == 2, "MDC", "PCC")) %>%
  filter(
    redcap_event_name == "consent_and_t1_sur_arm_1", 
    promis_record_id %in% t1$record_id)
```


```{r}
hrsn_data %<>%
  mutate(
    living_sit = ifelse(living_sit %in% c(2,3), 1, 0),
    living_prob = rowSums(across(living_probs___1:living_probs___7)),
    living_need = ifelse((living_sit + living_prob) > 0, 1, 0),
    food_worry = ifelse(food_worry %in% c(1, 2), 1, 0),
    food_last = ifelse(food_last %in% c(1, 2), 1, 0),
    food_need = ifelse((food_worry + food_last) > 0, 1, 0),
    transport = ifelse(transport == 1, 1, 0),
    utlities = ifelse(utlities %in% c(1, 2), 1, 0),
    fin_strain = ifelse(fin_strain %in% c(1, 2), 1, 0),
    help_daytoday = ifelse(help_daytoday %in% c(3, 4), 1, 0),
    lonely = ifelse(lonely > 3, 1, 0),
    social_need = ifelse((help_daytoday + lonely) > 0, 1, 0))

hrsn_data %<>%
  mutate(hrsn_need_score = rowSums(across(c(living_need, food_need, transport, utlities, fin_strain, social_need))))
```

```{r}
hrsn_data %>%
  select(
    living_need,
    food_need,
    transport,
    utlities,
    fin_strain,
    social_need,
    hrsn_need_score,
    site_type) %>%
  mutate(across(living_need:social_need, ~ factor(.x, levels = c(1, 0)))) %>%
  tbl_summary(
    by = site_type,
    value = everything() ~ "1",
    missing = "no",
    type = list(hrsn_need_score ~ "continuous"),
    statistic = list(hrsn_need_score ~ "{mean}, ({sd}); [{min}, {median}, {max}]"),
    label = list(transport ~ "transportation_need", utlities ~ "utilities_need")) %>%
  add_overall() %>% 
  add_p(
    all_continuous() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE)
  )
```