---
title: "AHRQ Long COVID - T1 Patient Survey Results"

date: "`r format(Sys.Date(), '%m-%d-%Y')`"

format: 
  docx:
    toc: true
    embed-resources: true
    reference-doc: "D:/custom-reference-doc.docx"

execute: 
  echo: false
---

```{r}
# Carlos Rodriguez, PhD. CU Dept. of Family Medicine
# 01-15-2026

# Patient Survey Data by Site Type

# Description - This script is a branch from the original patient_survey.qmd 
# file that has been modified to display all of the survey questions by 
# site_type (MDC or PCC).
```

```{r, message=FALSE, warning=FALSE}
library(magrittr, include = "%<>%")

library(dfmtbx)
# renv::install("carlosivanr/dfmtbx") # To update

library(tidyverse)
library(gtsummary)
```

```{r}
#| echo: false
# Participant accrual report draft
# Project ID = 33298
# Report ID = 176060
```

```{r}
# Loads pasc severity data and loads functions for displaying the tiles
source("d:/long_covid/scripts/functions/prep_redcap_data.R")
```

```{r}
#  Create a dataframe consisting of those that have consented
tab_data <- data %>%
  select(record_id, enrollstatus, patient_consent_form_complete, healthrelated_social_needs_complete) %>%
  group_by(record_id) %>%
  fill(enrollstatus, patient_consent_form_complete, healthrelated_social_needs_complete, .direction = "updown") %>%
  slice_head() %>%
  ungroup() %>%
  # Convert missing values in enrollstatus to Unknown/ could be not yet screened or contacted but no response
  mutate(
    across(enrollstatus:healthrelated_social_needs_complete, ~ ifelse(is.na(.x), "Unknown", .x))) %>%
  filter(patient_consent_form_complete == 1 | patient_consent_form_complete == "Complete")
```

```{r}
t1 <- data %>% filter(record_id %in% tab_data$record_id, redcap_event_name == "consent_and_t1_sur_arm_1")
t2 <- data %>% filter(record_id %in% tab_data$record_id, redcap_event_name == "t2_survey_arm_1")
```

# Patient demographics & characteristics
```{r}
# Patient age gender and sexual orientation
t1 %<>%
  mutate(age_group = case_when(
                               patient_age >= 18 & patient_age < 35 ~ "18-34",
                               patient_age >= 35 & patient_age < 65 ~ "35-64",
                               patient_age >= 65 ~ "65+",
                               TRUE ~ NA_character_
                               ),
         age_group = factor(age_group, levels = c("18-34", "35-64", "65+"), ordered = TRUE))
 
```

## Age, gender, sexual orientation
```{r}
# Patient age, gender and sexual orientation
t1 %>%
  select(site_type, age_group, patient_gender, patient_sexorient) %>%
  tbl_summary(
    by = site_type,
    # statistic = list(all_continuous() ~ "{mean} ({sd})"),
    label = list(
      age_group ~ "Age group",
      patient_gender ~ "Gender",
      patient_sexorient ~ "Sexual orientation"
    )
    ) %>%
    add_overall() %>% add_p()
```

## Race & ethnicity
```{r}
# Patient race and ethnicity
t1 %>%
  select(site_type, patient_race___1:patient_race___7, patient_ethn) %>%
  mutate(across(patient_race___1:patient_race___7, ~ factor(ifelse(is.na(.x), 0, 1), levels = c(0, 1)))) %>%
  tbl_summary(
    by = site_type,
    label = list(
      "patient_race___1" ~ "African American or Black",
      "patient_race___2" ~ "American Indian/Alaska Native.",
      "patient_race___3" ~ "Asian",
      "patient_race___4" ~ "Native Hawaiian/Other Pacific Islander",
      "patient_race___5" ~ "White",
      "patient_race___6" ~ "Other",
      "patient_race___7" ~ "Prefer not to answer",
      "patient_ethn" ~ "Hispanic"),
    value = list(patient_race___1 ~ "1",
                 patient_race___2 ~ "1",
                 patient_race___3 ~ "1",
                 patient_race___4 ~ "1",
                 patient_race___5 ~ "1",
                 patient_race___6 ~ "1",
                 patient_race___7 ~ "1")
  ) %>%
    add_overall() %>% add_p()
```

## Patient preferred language
```{r}
# Patient preferred language
t1 %>%
  select(site_type, patient_pref_lang) %>%
  tbl_summary(by = site_type,
    label = list("patient_pref_lang" ~ "Patient preferred lang.")
  ) %>%
    add_overall()
```

## Patient insurance
```{r}
# Patient race and ethnicity
t1 %>%
  select(site_type, patient_insurance___1:patient_insurance___10) %>%
  mutate(across(patient_insurance___1:patient_insurance___10, ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(
    by = site_type,
    label = list(
      "patient_insurance___1" ~ "State market place",
      "patient_insurance___2" ~ "Employer provided",
      "patient_insurance___3" ~ "Medicaid",
      "patient_insurance___4" ~ "Medicare - Original Medicare",
      "patient_insurance___5" ~ "Medicare - Advantage Plan",
      "patient_insurance___6" ~ "Worker's Comp",
      "patient_insurance___7" ~ "Other",
      "patient_insurance___8" ~ "Self-pay",
      "patient_insurance___9" ~ "Uninsured",
      "patient_insurance___10" ~ "Prefer not to answer",
      "patient_insurance___11" ~ "Medigap",
      "patient_insurance___12" ~ "Medicare Part D"
    ),
    value = everything() ~ "1"
  ) %>%
    add_overall() %>% add_p()
```

## Patient education level
```{r}
# Patient education level
t1 %>%
  select(patient_school, site_type) %>%
  tbl_summary(by = site_type,
    label = list(patient_school ~ "Patient education level")
  ) %>%
    add_overall() %>% add_p()
```

## Patient marital status
```{r}
t1 %>%
  select(patient_marital, site_type) %>%
  tbl_summary(by = site_type,
    label = list(patient_marital ~ "Patient marital status")
  ) %>%
    add_overall() %>% add_p()
```

## Patient employment status pre- long COVID
```{r}
t1 %>%
  select(site_type, patient_employ___1:patient_employ___7) %>%
  mutate(across(patient_employ___1:patient_employ___7, ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary( by = site_type,
    label = list(
      patient_employ___1 ~ "Employed Full-time",
      patient_employ___2 ~ "Employed Part-time",
      patient_employ___3 ~ "Unemployed",
      patient_employ___4 ~ "Disabled",
      patient_employ___5 ~ "Retired",
      patient_employ___6 ~ "Student",
      patient_employ___7 ~ "Other"
    ),
    value = everything() ~ "1"
  ) %>%
  add_overall() %>% add_p()
```

## Patient employment status current
```{r}
t1 %>%
  select(site_type, patient_employ_2___1:patient_employ_2___7) %>%
  mutate(across(patient_employ_2___1:patient_employ_2___7, ~ factor(.x, levels = c(0,1)))) %>%
  tbl_summary(by = site_type,
    label = list(
      patient_employ_2___1 ~ "Employed Full-time",
      patient_employ_2___2 ~ "Employed Part-time",
      patient_employ_2___3 ~ "Unemployed",
      patient_employ_2___4 ~ "Disabled",
      patient_employ_2___5 ~ "Retired",
      patient_employ_2___6 ~ "Student",
      patient_employ_2___7 ~ "Other"
      ),
    value = everything() ~ "1"
  ) %>%
  add_overall() %>% add_p()
```

# Patient clinical questions
* Currently subsets to those that provided consent.

## 	For how many months do you feel you have had Long COVID symptoms (regardless of formal diagnosis)? (For example, 1 year would be 12 months; 2 years would be 24 months; 3 years would be 36 months) 
```{r}
t1 %>%
  select(months_symps, site_type) %>%
  tbl_summary(by = site_type,
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  ) %>%
  add_overall() %>% 
  add_p(
    everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE))
```

## Do you now have a diagnosis from a health care provider of Long COVID?
```{r}
t1 %>%
  select(lcdiagnosis, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### If yes, how many months did it take for you to get that diagnosis after your symptoms started? (For example, 1 year would be 12 months; 2 years would be 24 months; 3 years would be 36 months)
```{r}
t1 %>%
  filter(lcdiagnosis == 1) %>%
  select(
    site_type,
    ifyes_monthsymps) %>%
  tbl_summary(by = site_type,
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  ) %>%
  add_overall() %>% 
  add_p(
    everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE)
  )
```

## 	Which of the following conditions had you been diagnosed with prior to (before) developing Long COVID symptoms? (check all that apply)
```{r}
# Order the condition from most frequent to least frequent
ordered_conditions <- t1 %>% 
  select(conditions___1:conditions___14) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(cols = everything(), names_to = "condition", values_to = "count") %>%
  arrange(desc(count)) %>%
  pull(condition)
```

```{r}
t1 %>%
  # select(conditions___1:conditions___14) %>%
  select(site_type, all_of(ordered_conditions)) %>%
  tbl_summary(by = site_type,
    label = list(
      "conditions___1" ~ "Hypertension",
      "conditions___2" ~ "Obesity",
      "conditions___3" ~ "Chronic lung disease (COPD, asthma, pulmonary fibrosis)",
      "conditions___4" ~ "Diabetes Mellitus",
      "conditions___5" ~ "Chronic immune suppression (organ transplant, HIV)",
      "conditions___6" ~ "Coronary artery disease",
      "conditions___7" ~ "High cholesterol",
      "conditions___8" ~ "Heart arrhythmias",
      "conditions___9" ~ "Major depression",
      "conditions___10" ~ "Anxiety",
      "conditions___11" ~ "PTSD",
      "conditions___12" ~ "Cancer",
      "conditions___13" ~ "Other (please describe)",
      "conditions___14" ~ "None"),
    value = everything() ~ "1"
  ) %>%
  add_overall() %>% 
  add_p()
```


```{r}
# All who selected "Other" did not provide free text so far
# commented here 
other_condition_n <- t1 %>%
  filter(conditions___14 == 1) %>%
  select(conditions_other) %>%
  drop_na() %>%
  nrow()

if (other_condition_n >= 1) {
  t1 %>%
    filter(conditions___14 == 1) %>%
    select(conditions_other) %>%
    tbl_summary()
}
```

## Have you received or increased your dose of any of the following medications specifically for Long COVID or Long COVID symptoms? (select all that apply)
```{r}
# Order the medications from most frequent to least frequent
# t1 %<>% 
#   mutate(across(medications___1:medications___13, ~ factor(ifelse(.x == "Checked", 1, 0), levels = c(0, 1))))

ordered_medications <- t1 %>% 
  select(medications___1:medications___13) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(cols = everything(), names_to = "medication", values_to = "count") %>%
  arrange(desc(count)) %>%
  pull(medication)
``` 

```{r}
t1 %>%
  # select(medications___1:medications___13) %>%
  select(site_type, all_of(ordered_medications)) %>%  
  tbl_summary(by = site_type,
    label = list(
      "medications___1" ~ "Paxlovid",
      "medications___2" ~ "Low dose naltrexone",
      "medications___3" ~ "Heart rate controlling agents (beta-blockers, calcium channel blockers, ivabradine)",
      "medications___4" ~ "Prednisone",
      "medications___5" ~ "Lung inhaler medications (Symbicort, Advair/Wixela, Breo)",
      "medications___6" ~ "Midodrine",
      "medications___7" ~ "Fludricortisone",
      "medications___8" ~ "SSRIs/SNRIs",
      "medications___9" ~ "Memantine",
      "medications___10" ~ "Adderall/Ritalin",
      "medications___11" ~ "Modafinil",
      "medications___12" ~ "Other (please specify)",
      "medications___13" ~ "None"),
    value = everything() ~ "1"
  ) %>%
    add_overall() %>% add_p()
```

### Other medicine (please specify)
```{r}
# All who selected "Other" 
other_medication_n <- t1 %>%
  filter(medications___13 == 1) %>%
  select(other_med) %>%
  drop_na() %>%
  nrow()

if (other_medication_n >= 1) {
  t1 %>%
    filter(medications___13 == 1) %>%
    select(other_med) %>%
    tbl_summary()
}
```

## Have you received any of the following therapies specifically for Long COVID or Long COVID symptoms? (select all that apply)
```{r}
# t1 %<>%
#   mutate(across(therapies___13:therapies___21, ~ factor(ifelse(.x == "Checked", 1, 0), levels = c(0, 1))))

ordered_therapies <- t1 %>%
  select(therapies___13:therapies___21) %>%
  mutate(across(everything(), ~ as.numeric(.x))) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(cols = everything(), names_to = "therapy", values_to = "count") %>%
  arrange(desc(count)) %>%
  pull(therapy)
``` 

```{r}
t1 %>%
  # select(therapies___13:therapies___21) %>%
  select(site_type, all_of(ordered_therapies)) %>%
  tbl_summary(by = site_type,
    label = list(
      "therapies___13" ~ "Speech therapy/cognitive training",
      "therapies___14" ~ "Physical therapy",
      "therapies___15" ~ "Occupational therapy",
      "therapies___16" ~ "Group therapy/peer support",
      "therapies___17" ~ "Pulmonary rehab",
      "therapies___18" ~ "Counseling/mental or behavioral health therapy",
      "therapies___19" ~ "Complementary/alternative therapies (examples like acupuncture, supplements, chiropractic, etc.)",
      "therapies___20" ~ "Other (please specify)",
      "therapies___21" ~ "None"),
    value = everything() ~ "1"
  ) %>%
  add_overall() %>% 
  add_p()
```

## Other services (please specify)
```{r}
# All who selected "Other" 
other_therapies_n <- t1 %>%
  filter(therapies___20 == 1) %>%
  select(other_med) %>%
  drop_na() %>%
  nrow()

if (other_therapies_n >= 1) {
  t1 %>%
    filter(therapies___20 == 1) %>%
    select(other_service) %>%
    tbl_summary()
}
```

# PROMIS Global Health
## Global physical and mental health subscores
* PROMIS physical health and mental health subscores range from 4 (min) - 20 (max)
```{r}
t1 %>%
  select(site_type, promis_global_phys, promis_global_ment) %>%
  tbl_summary(site_type,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      promis_global_phys ~ "Global physical health",
      promis_global_ment ~ "Global mental health"
    )
  ) %>%
  add_overall() %>%
  add_p(everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE))
```

## Promis Global Health Physical and Mental Health T-Scores
```{r}
# Display the tables of T-Score and their averages
t1 %>%
  select(site_type, promis_pht, promis_mht) %>%
  tbl_summary(by = site_type,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
      promis_pht ~ "Global physical health T-score",
      promis_mht ~ "Global mental health T-score"
      # promis_global01 ~ "In general, would you say your health is:",
      # promis_global09r ~ "In general, please rate how well you carry out your usual social activities and roles."
    )
  ) %>%
  add_overall() %>% 
  add_p(
    everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE)
  )
```

## In general, would you say your health is:
```{r}
t1 %>%
  select(site_type, promis_global01) %>%
  tbl_summary(by = site_type,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
    )
  ) %>%
    add_overall() %>% add_p()
```


## In general, please rate how well you carry out your usual social activities and roles.
```{r}
t1 %>%
  select(promis_9, site_type) %>%
  tbl_summary(by = site_type,
    statistic = all_continuous() ~ "{mean} ({sd}); [{min}, {median}, {max}]",
    label = list(
    )
  ) %>%
    add_overall() %>% add_p()
```


# PASC
## Do you think you currently have symptoms or health problems resulting from your COVID infection?
```{r}
t1 %>%
  select(ps_ptpasc, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

## Symptoms
* n.b. denominator is a subset to those that answered "Yes" to the question "Do you think you currently have symptoms or health problems resulting from your COVID infection?"
* n.b. denominator for ps_menstrual and ps_menopause is a subset to the above and a response of "Female", "Transgender Male", "Non-binary", "Other, please describe", or "Prefer not to answer" to the question What is your gender identity?

### Overall
```{r}
# This chunk begins the section for generating the multi-colored figure in the
# report.
core_symptoms <- t1 %>%
  select(ps_fatigue:ps_sex) %>%
  names()

# Another option is to display as a chart with binary responses
pasc_hist <- t1 %>%
  filter(ps_ptpasc == "Yes") %>%
  select(all_of(core_symptoms)) %>%
  mutate(across(everything(), ~ ifelse(str_detect(.x, "Yes"), 1, 0))) %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "yes") %>%
  group_by(symptom) %>%
  summarise(total_endorsed = sum(yes)) %>%
  mutate(symptom = factor(symptom, levels = core_symptoms))
 
# Get a denominator all patients
denominator_all <- t1 %>%
  filter(ps_ptpasc == "Yes") %>%
  nrow()

# Get a denominator for ps_menstrual:ps_menopause which is a subset of those
# that are not Male or Transgender Female
denominator_subset <- t1 %>%
  filter(ps_ptpasc == "Yes") %>%
  filter(!patient_gender %in% c("Male", "Transgender Female")) %>%
  select(patient_gender, ps_menstrual:ps_menopause) %>%
  nrow()

pasc_hist %<>%
  mutate(percent = str_c("(",
    round(
      ifelse(symptom %in% c("ps_menstrual", "ps_menopause"), total_endorsed / denominator_subset, total_endorsed / denominator_all),
      2) * 100, "%)")) %>%
  mutate(n_per = str_c(total_endorsed, " ", percent))

ordered_symptoms <- pasc_hist %>%
  arrange(total_endorsed) %>%
  pull(symptom)
```

```{r, fig.height = 6.5, fig.width=6.5, fig.dpi = 600}
pasc_hist %>%
  mutate(symptom = factor(symptom, levels = ordered_symptoms)) %>%
  ggplot(aes(x = symptom, y = total_endorsed, fill = symptom)) +
  geom_col() +
  geom_text(
    aes(label = n_per), 
          hjust = -0.25,
          size = 3) +  
  theme_minimal() +
  lims(y = c(0, 60)) +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x = "Symptom", y = "Number endorsed (percent)")
```


### MDC
```{r}
core_symptoms <- t1 %>%
  select(ps_fatigue:ps_sex) %>%
  names()

# Another option is to display as a chart with binary responses
pasc_hist <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "MDC") %>%
  select(all_of(core_symptoms)) %>%
  mutate(across(everything(), ~ ifelse(str_detect(.x, "Yes"), 1, 0))) %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "yes") %>%
  group_by(symptom) %>%
  summarise(total_endorsed = sum(yes)) %>%
  mutate(symptom = factor(symptom, levels = core_symptoms))
 
# Get a denominator all patients
denominator_all <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "MDC") %>%
  nrow()

# Get a denominator for ps_menstrual:ps_menopause which is a subset of those
# that are not Male or Transgender Female
denominator_subset <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "MDC") %>%
  filter(!patient_gender %in% c("Male", "Transgender Female")) %>%
  select(patient_gender, ps_menstrual:ps_menopause) %>%
  nrow()

pasc_hist %<>%
  mutate(percent = str_c("(",
    round(
      ifelse(symptom %in% c("ps_menstrual", "ps_menopause"), total_endorsed / denominator_subset, total_endorsed / denominator_all),
      2) * 100, "%)")) %>%
  mutate(n_per = str_c(total_endorsed, " ", percent))

ordered_symptoms <- pasc_hist %>%
  arrange(total_endorsed) %>%
  pull(symptom)
```

```{r, fig.height = 6.5, fig.width=6.5, fig.dpi = 600}
pasc_hist %>%
  mutate(symptom = factor(symptom, levels = ordered_symptoms)) %>%
  ggplot(aes(x = symptom, y = total_endorsed, fill = symptom)) +
  geom_col() +
  geom_text(
    aes(label = n_per), 
          hjust = -0.25,
          size = 3) +  
  theme_minimal() +
  lims(y = c(0, 35)) +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x = "Symptom", y = "Number endorsed (percent)")
```

### PCC
```{r}
core_symptoms <- t1 %>%
  select(ps_fatigue:ps_sex) %>%
  names()

# Another option is to display as a chart with binary responses
pasc_hist <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "PCC") %>%
  select(all_of(core_symptoms)) %>%
  mutate(across(everything(), ~ ifelse(str_detect(.x, "Yes"), 1, 0))) %>%
  pivot_longer(cols = everything(), names_to = "symptom", values_to = "yes") %>%
  group_by(symptom) %>%
  summarise(total_endorsed = sum(yes)) %>%
  mutate(symptom = factor(symptom, levels = core_symptoms))
 
# Get a denominator all patients
denominator_all <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "PCC") %>%
  nrow()

# Get a denominator for ps_menstrual:ps_menopause which is a subset of those
# that are not Male or Transgender Female
denominator_subset <- t1 %>%
  filter(ps_ptpasc == "Yes", site_type == "PCC") %>%
  filter(!patient_gender %in% c("Male", "Transgender Female")) %>%
  select(patient_gender, ps_menstrual:ps_menopause) %>%
  nrow()

pasc_hist %<>%
  mutate(percent = str_c("(",
    round(
      ifelse(symptom %in% c("ps_menstrual", "ps_menopause"), total_endorsed / denominator_subset, total_endorsed / denominator_all),
      2) * 100, "%)")) %>%
  mutate(n_per = str_c(total_endorsed, " ", percent))

ordered_symptoms <- pasc_hist %>%
  arrange(total_endorsed) %>%
  pull(symptom)
```

```{r, fig.height = 6.5, fig.width=6.5, fig.dpi = 600}
pasc_hist %>%
  mutate(symptom = factor(symptom, levels = ordered_symptoms)) %>%
  ggplot(aes(x = symptom, y = total_endorsed, fill = symptom)) +
  geom_col() +
  geom_text(
    aes(label = n_per), 
          hjust = -0.25,
          size = 3) +  
  theme_minimal() +
  lims(y = c(0, 35)) +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x = "Symptom", y = "Number endorsed (percent)")
```

```{r}
# These are the 12 symptoms used to calculate a PASC score
pasc_symptoms <- c(
"ps_sense",
"ps_malaise",
"ps_cough",
"ps_think",
"ps_thirst",
"ps_heart",
"ps_pain",
"ps_fatigue",
"ps_sex",
"ps_faint",
"ps_gastro",
"ps_nerve")

# These are the weights to multiply each binary symptom value
pasc_symptom_scores <- c(8, 7, 4, 3, 3, 2, 2, 1, 1, 1, 1, 1)
```

## PASC Scores
```{r}
# Multiply each symptom column with the corresponding symptom weight then merge 
# the data back into the main t1 data frame when filtered, only to those that
# had the pasc administered. Merging into the filtered t1 data frame was 
# performed in case study team wants to see the scores broken out by clinic
# gender, age, or some other variable.
t1 %>%
  filter(ps_ptpasc == "Yes") %>%
  select(site_type, pasc_score, pasc_positive) %>%
  tbl_summary(by = site_type,
    statistic = list(pasc_score ~ "{mean} ({sd}); [{min}, {median}, {max}]"),
    value = list(pasc_positive ~ "1")
  ) %>%
  add_overall() %>% 
  add_p(
    everything() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE)
  )
```

<!-- TILE PLOTS -->
## Average symptom burden, severity, and frequency
* Symptoms ordered by frequency as in the previous chart
* All burden, severity, and frequency questions are branched and presented only if patient responded endorsed experiencing the given symptom.
* "ps_sense", "ps_headache", "ps_itching", "ps_bald", "ps_menstrual", "ps_menopause", "ps_fertility" "ps_sex" not assessed for frequency or severity.
```{r}
# Loads pasc severity data and loads functions for displaying the tiles
source("d:/long_covid/scripts/functions/prep_severity_data.R")
```

```{r}
# Filter severity data to the subjects of interest
pasc_severity_data <- pasc_severity_data %>%
  filter(record_id %in% t1$record_id, redcap_event_name == "consent_and_t1_sur_arm_1")
```

```{r}
# Join the site_type variable for filtering
pasc_severity_data <- pasc_severity_data %>%
  left_join(
    t1 %>% select(record_id, site_type),
    by = "record_id")
```

### Overall
```{r, fig.height = 8, fig.width=6.5, fig.dpi = 600}
pasc_severity_data %>%
  make_pasc_tile_plot(., "ps")
```

### MDC
```{r, fig.height = 8, fig.width=6.5, fig.dpi = 600}
pasc_severity_data %>%
  filter(site_type == "MDC") %>%
  make_pasc_tile_plot(., "ps")
```

### PCC
```{r, fig.height = 8, fig.width=6.5, fig.dpi = 600}
pasc_severity_data %>%
  filter(site_type == "PCC") %>%
  make_pasc_tile_plot(., "ps")
```

# Experiences of Stigma
## Have you had one or more appointments with medical providers at a primary care clinic in the past three months?
```{r}
t1 %>%
  select(pcc_appts, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```


## Mean score of "lack of understanding" scale from Illness Invalidation Inventory for experiences with PCC appointments
* n.b. Subsets to those that answered "Yes" to the question "Have you had one or more appointments with medical providers at a primary care clinic in the past three months?"
* Scale ranges from 1(min) to 5(max), with 1 indicating the lowest perceived understanding from medical providers and 5 indicated the highest perceived understanding.

```{r}
t1 %>%
  filter(pcc_appts == "Yes") %>%
  select(lou_score_pcc) %>%
  tbl_summary(
    type = everything() ~ "continuous",
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  )
```


<!-- INDIVIDUAL SCORES -->
## Individual questions: How often in the past 3 months did medical professionals at your primary care clinic react to you in the following ways:
### Medical professionals took me seriously.
```{r}
t1 %>%
  filter(pcc_appts == "Yes") %>%
  select(serious_pcc, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Medical professionals understood the consequences of my health problems or illness.
```{r}
t1 %>%
  filter(pcc_appts == "Yes") %>%
  select(consequences_pcc, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Medical professionals gave me the chance to talk about what is on my mind.
```{r}
t1 %>%
  filter(pcc_appts == "Yes") %>%
  select(talk_pcc, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```


<!-- EXPERIENCES WITH MDC -->
## Have you had one or more appointments with medical providers at a multi-disciplinary Long COVID clinic in the past three months?
```{r}
t1 %>%
  select(mdc_appts, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

## Mean score of “lack of understanding” scale from Illness Invalidation Inventory for experiences with MDC appointments
•	n.b. Subsets to those that answered “Yes” to the question “Have you had one or more appointments with medical providers at a multi-disciplinary care clinic in the past three months?”
•	Scale ranges from 1(min) to 5(max), with 1 indicating the lowest perceived understanding from medical providers and 5 indicated the highest perceived understanding.

```{r}
t1 %>%
  filter(mdc_appts == "Yes") %>%
  select(lou_score_mdc) %>%
  tbl_summary(
    type = everything() ~ "continuous",
    statistic = everything() ~ "{mean} ({sd}); [{min}, {median}, {max}]"
  )
```

<!-- INDIVIDUAL SCORES -->
## Individual questions: How often in the past 3 months did medical professionals at your multi-disciplinary Long COVID clinic react to you in the following ways:
```{r}
t1 %>%
  filter(mdc_appts == "Yes") %>%
  select(serious_mdc, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Medical professionals understood the consequences of my health problems or illness.
```{r}
t1 %>%
  filter(mdc_appts == "Yes") %>%
  select(consequences_mdc, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Medical professionals gave me the chance to talk about what is on my mind.
```{r}
t1 %>%
  filter(mdc_appts == "Yes") %>%
  select(talk_mdc, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```


# Health Related Social Needs
## Living Situation
### What is your living situation today?
```{r}
t1 %>%
  select(living_sit, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Think about the place you live. Do you have problems with any of the following?
```{r}
t1 %>%
  select(living_probs___1:living_probs___8, site_type) %>%
  tbl_summary(
    by = site_type,
    value = everything() ~ "1",
    label = list(
      living_probs___1 ~ "Pests such as bugs, ants, or mice",
      living_probs___2 ~ "Mold",
      living_probs___3 ~ "Lead paint or pipes",
      living_probs___4 ~ "Lack of heat",
      living_probs___5 ~ "Oven or stove not working",
      living_probs___6 ~ "Smoke detectors missing or not working",
      living_probs___7 ~ "Water leaks",
      living_probs___8 ~ "None of the above"
    )
  ) %>%
  add_overall() %>% 
  add_p()
```

## Food
### Within the past 12 months, were you worried that your food would run out before you got money to buy more?
```{r}
t1 %>%
  select(food_worry, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

### Within the past 12 months, has the food you bought just didn't last and you didn't have money to get more?
```{r}
t1 %>%
  select(food_last, site_type) %>%
  tbl_summary(by = site_type) %>%
  add_overall() %>% 
  add_p()
```

## Transportation
### In the past 12 months, has lack of reliable transportation kept you from medical appointments, meetings, work or from getting things needed for daily living?
```{r}
t1 %>%
  select(transport, site_type) %>%
  tbl_summary( 
    by = site_type,
    type = list(transport ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

## Utilities
### In the past 12 months has the electric, gas, oil, or water company threatened to shut off services in your home?
```{r}
t1 %>%
  select(utlities, site_type) %>%
  tbl_summary(
    by = site_type,
    type = list(utlities ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

## Financial Strain
### How hard is it for you to pay for the very basics like food, housing, medical care, and heating? Would you say it is:
```{r}
t1 %>%
  select(fin_strain, site_type) %>%
  tbl_summary( 
    by = site_type,
    type = list(fin_strain ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

## Family & Community Support
### If for any reason you need help with day-to-day activities such as bathing, preparing meals, shopping, managing finances, etc., do you get the help you need?
```{r}
t1 %>%
  select(help_daytoday, site_type) %>%
  tbl_summary( by = site_type,
    type = list(help_daytoday ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

### How often do you feel lonely or isolated from those around you?
```{r}
t1 %>%
  select(lonely, site_type) %>%
  tbl_summary( by = site_type,
    type = list(lonely ~ "categorical")
  ) %>%
  add_overall() %>% 
  add_p()
```

## Summary of needs by domain
```{r}
t1 %>%
  filter(site_type %in% c("MDC", "PCC")) %>%
  select(
    living_need,
    food_need,
    transport_need,
    utlities_need,
    fin_strain_need,
    social_need,
    hrsn_need_score,
    site_type) %>%
  tbl_summary(
    by = site_type,
    value = everything() ~ "1",
    missing = "no",
    type = list(hrsn_need_score ~ "continuous"),
    statistic = list(hrsn_need_score ~ "{mean}, ({sd}); [{min}, {median}, {max}]"),
    label = list(
      transport_need ~ "transportation_need", 
      utlities_need ~ "utilities_need")) %>%
  add_overall() %>% 
  add_p(
    all_continuous() ~ "t.test",
    test.args = all_tests("t.test") ~ list(var.equal = TRUE)
  )
```
